---
title: "M21_202607_preprocessing"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

\scriptsize
# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```


Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```

# Load Files and Format Files  {-}

## Load Files 

```{r load_files}
#DIR <- "csv_files"
df_a <- read_csv("rt_data_hc_A.csv")
df_b <- read_csv( "rt_data_hc_B_fixed.csv")
frq_w <- read_csv("frq_cw.csv")
frq_nw <- read_csv("frq_nw.csv")
dmg <- read_csv("demo_lang_vsl_pca_hc.csv")

erp_2A <- read_csv("fs_m21_ldt_mea_200300_050050_1_AB.csv")
erp_2B <- read_csv("fs_m21_ldt_mea_200300_050050_1_BA.csv")
erp_4A <- read_csv("fs_m21_ldt_mea_300500_050050_1_AB.csv")
erp_4B <- read_csv("fs_m21_ldt_mea_300500_050050_1_BA.csv")
```

```{r}
# Concatenate datasets
rt <- bind_rows(AB = df_a, 
                BA = df_b,
               .id = "List")
rt_dmg<- right_join(dmg, rt, join_by(SubjID == subject_nr)) |>  # Join Participant Demographic and Lang Data
                    mutate(target = tolower(target)) |>
                    filter(correct == 1)

# Divide into Experimental and Filler Items
rt_fill <- rt_dmg |> filter(str_detect(targ_type, "^FILL"))
rt_exp <- rt_dmg |> filter(!str_detect(targ_type, "^FILL"))

# Add logFS to frequency datasets
frq_w <- frq_w |> mutate(Log10FS = log10(FS))
frq_nw <- frq_nw |> mutate(Log10FS = log10(FS))

frq_w <- frq_w |> mutate(LogFS = log(FS))
frq_nw <- frq_nw |> mutate(LogFS = log(FS))

# Define Factors and Conditions
rt_exp_format <- rt_exp |>
  separate(targ_type, into = c("trial_type", "family_size", "complexity"), sep = "_",
           remove = TRUE,
           extra = "drop",
           fill = "right")

# Divide into Words and Nonwords
rt_words <- rt_exp_format |> filter(trial_type == "CW") |> select(- complexity) 
rt_nwords <- rt_exp_format |> filter(trial_type == "NW")

# Join Stimulus Frequency Data
rt_words_frq <- left_join(rt_words, frq_w, join_by(target))|>
  select(-cond_trig.y, -word_trig.y) |>
  rename(cond_trig = cond_trig.x, word_trig = word_trig.x)  # remove duplicate columns
rt_nwords_frq <-  left_join(rt_nwords, frq_nw, join_by(target==word)) |>   
  select(-cond_trig.y, -word_trig.y, -List.y) |>
  rename(cond_trig = cond_trig.x, word_trig = word_trig.x, List = List.x)  

rt_words_frq2 <- rt_words_frq |> select(SubjID, z_vcb, z_spl, z_art, Dim.1, Dim.2, correct, response_time,
                                        trial_type, target, word_trig, cond_trig, Base,affix, FS, BF, LogFS,LogBF, 
                                        BaseLength, WholeFormLength, List)
rt_nwords_frq2 <- rt_nwords_frq |> select(SubjID, z_vcb, z_spl, z_art, Dim.1, Dim.2, correct, response_time,
                                        trial_type, complexity, target, ItemID, word_trig, cond_trig, base,affix, FS, BF, LogFS,LogBF, 
                                        BaseLength, WholeFormLength, List)
```

```{r}
# Join lists
erp_2i <- bind_rows(
  erp_2A |> mutate(List = "AB"),
  erp_2B |> mutate(List = "BA")
)

erp_4i <- bind_rows(
  erp_4A |> mutate(List = "AB"),
  erp_4B |> mutate(List = "BA")
)



# Now join both time windows
erp_FS <- bind_rows(
  erp_2i |> mutate(time_window = "N250"),
  erp_4i |> mutate(time_window = "N400")
)


# Now we extract `SubjID` from the `ERPset` column

erp_FS_i <- erp_FS |>
  rename(SubjID = ERPset) |>
  mutate(SubjID = str_replace(SubjID, "_LDT_diff_waves", "")) |>
  mutate(binlabel = str_replace(binlabel, "Critical_", "")) |>
  mutate(binlabel = str_replace(binlabel, "_family", "")) |>
  select(-mlabel)


erp_dmg <- erp_FS_i |>
  left_join(dmg, by = "SubjID") |>
  select(SubjID, everything()) 
```

Then we do some more formatting and cleanup of the dataframes.We  create separate columns, one for each independent variable (anteriority, laterality, morphological family size). To do this we have to use `seperate` function from the `stringr` package. Run `vignette("programming", package = "dplyr")` to see more about `tidy-selection` and `tidy-evaluation`.



```{r}
erp_dmg_words <- erp_dmg |> filter(bini %in% c(1:2)) |>
  select(SubjID, value,chindex,chlabel,bini,binlabel,List,time_window,z_vcb,z_spl,z_art,Dim.1,Dim.2)
erp_dmg_nonwords <- erp_dmg |> filter(bini %in% c(3:6)) |>
  select(SubjID, value,chindex,chlabel,bini,binlabel,List,time_window,z_vcb,z_spl,z_art,Dim.1,Dim.2)

# Words
erp_dmg_words <- erp_dmg_words |>
  separate(binlabel, into = c("trial_type","family_size"), sep = "_", remove = TRUE) |>
  select(-trial_type)

erp_dmg_words$family_size[erp_dmg_words$family_size == "large"] <- "Large"
erp_dmg_words$family_size[erp_dmg_words$family_size == "small"] <- "Small"


# Nonwords
erp_dmg_nonwords <- erp_dmg_nonwords |>
  separate(binlabel, into = c("trial_type", "family_size", "complexity"), sep = "_", remove = TRUE) |>
  select(-trial_type)

erp_dmg_nonwords$complexity[erp_dmg_nonwords$complexity == "complex"] <- "Complex"
erp_dmg_nonwords$complexity[erp_dmg_nonwords$complexity == "simple"] <- "Simple"
erp_dmg_nonwords$family_size[erp_dmg_nonwords$family_size == "large"] <- "Large"
erp_dmg_nonwords$family_size[erp_dmg_nonwords$family_size == "small"] <- "Small"

# Format as factors
erp_dmg_nonwords <- erp_dmg_nonwords |>
  mutate(complexity = fct_relevel(complexity, "Simple", "Complex"))

erp_dmg_nonwords <- erp_dmg_nonwords |>
  mutate(family_size = fct_relevel(family_size, "Small", "Large"))


write_csv(erp_dmg_words, "erp_fs_dmg_words.csv")
write_csv(erp_dmg_nonwords, "erp_fs_dmg_nonwords.csv")

write_csv(rt_words_frq2, "rt_words_frq.csv")
write_csv(rt_nwords_frq2, "rt_nwords_frq.csv")
```

