---
title: "twoway"
author: "Joanna Morris"
date: '2022-04-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE)
```

## Load Data and Check Variables

We’ll use the data that show there is a significant interaction, as seen here, also found in Chapter 16 Data Set 1 (ch16ds1.csv)

```{r readFile}
library(readr)
ch16ds1 <- read_csv("ch16ds1.csv")
```

Let’s double-check the means for each of the four groups: Female in High Impact, Female in Low Impact, Male in High Impact, and Male in Low Impact. We should get the same numbers as found in Table 16.3. For this we will use a handy function in the `psych` package called `describeBy()`.We can see in this output that we have 10 people in each group, and the means are what we expect.

```{r examineVariables}
library(psych)
describeBy(ch16ds1$Loss, group = list(ch16ds1$Treatment, ch16ds1$Gender))
```

# Run ANOVA

Use the `aov` function to calculate the source table and F. But before we do that, we want to tell R to change the way it is comparing the groups. There are easily half a dozen ways in which we can mathematically compare our groups. We are going to use `Helmert` contrast, and we only need to set it once for all ANOVAs we run during a single R session. 


```{r set_anova_options}
options(contrasts = c("contr.helmert", "contr.poly")) 
options("contrasts")
```

After we tell R we want to use a Helmert contrast (`contr. helmert`) for categorical variables and polynomial contrasts for ordered variables (`contr.poly`), we can now run our ANOVA.

```{r runAnova}
m1 <- aov(Loss ~ Treatment*Gender, data = ch16ds1)
# m2 <- aov(Loss ~ Treatment * Gender, data = ch16ds1)
```

`m1`: the name of the R object that is storing our results
`<-`: the characters that assign our results to `m1`

 `m1` <- `aov(Loss ~ Treatment + Gender + Treatment*Gender, data = ch16ds1)`

`aov`: the function to run ANOVA

`Loss`: our dependent variable

`~`: in shorthand, it means explained by or equal to.

`Treatment + Gender + Treatment\*Gender`: we are telling aov that the independent variables are `Treatment`, `Gender`, and the interaction between `Treatment` and `Gender` that we get by multiplying (`\*`) `Treatment` by `Gender`.
`data = ch16ds1`: use this data object.

We then use the function `Anova()` from the `car` package with the argument `type = III` to get the source table.

```{r sourceTable}
library(car)
# summary(m1)
Anova(m1, type = "III")
```

To determine whether we can trust our results based on F, we need to check the assumption of equal variances across groups. The null hypothesis is that all group means are equal, and we hope to fail to reject the null. We will use .05 as our significance level.

```{r checkVariances}
library(car)
leveneTest(Loss ~ Treatment*Gender, data = ch16ds1)
```

Based on $F(3, 36) = 2.09, p = .12$, which has a probability > .05, we will fail to reject the null and we can trust the results because we have met the assumption of equal variance.

#Plot Means

Create an interaction plot for all four groups. For this first example of an interaction plot, we are using as many of the default options as possible. So, we just need to tell the function what variable to use for the x-axis (`x.factor`), what variable to use for the y-axis (`response`), and what variable to use for each line (`trace.factor`) along with what type of number we are plotting. By default, interaction.plot will plot the means of each group

```{r interactionPlot}
interaction.plot(x.factor = ch16ds1$Treatment, trace.factor = ch16ds1$Gender, response = ch16ds1$Loss, xlab = "Treatment", ylab = "Loss", trace.label = "Gender")
```

# Compare Groups
Finally, use the `TukeyHSD` function to compare groups. Because we now have a factorial ANOVA with two factors and interaction, TukeyHSD output has gotten a lot bigger.

```{r compareGroups}
TukeyHSD(m1)
```

