---
title: "M21_202601"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---


\scriptsize
# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```


Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```


1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette_1 <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# set emm options
emm_options(pbkrtest.limit = 4671)

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```




## A. RT — Words (primary behavioral model)

**Question:**
Does orthographic sensitivity predict efficiency, controlling lexical familiarity?

```{r}
library(lme4)

rt_w <- read.csv("rt_words_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )


m_rt_words <- lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    zLogBF:OS + zLogFS:OS +
    (1 + zLogBF + zLogFS | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_rt_words)
```

**Report:** main effects + OS moderation only.
LP is included but not emphasized.

---

## B. RT — Nonwords (primary behavioral model)

**Question:**
Does morphological complexity slow decisions, and is this cost modulated by OS?

```{r}
rt_nw <- read.csv("rt_nwords_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity),  # SIMP / COMP
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    complexity:OS +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_rt_nw)
```

---

## C. ERP — Words

Run **separately by time window** (this is important).

### C1. N250 — Words

**Question:**
Does orthographic sensitivity modulate early sensitivity to morphological family structure?

```{r}
erp_w <- read.csv("erp_dmg_words.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# ERP words
contrasts(erp_w$family_size) <- contr.sum(2)

m_w_N250 <- lmer(
  value ~ family_size*OS + family_size*LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_w_N250)
```

**Follow-up (only if interaction significant):**

```{r}
library(emmeans)
emmeans(m_w_N250, ~ family_size | OS,
        at = list(OS = c(-1, 0, 1)))
```

---

### C2. N400 — Words

**Question:**
Does language proficiency shape semantic integration of family structure?

```{r}
m_w_N400 <- lmer(
  value ~ family_size*LP + family_size*OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_w_N400)
```

**Follow-up (core result):**

```{r}
emmeans(m_w_N400, ~ family_size | LP,
        at = list(LP = c(-1, 0, 1)))
```
```{r}
emmeans(m_w_N400, ~ family_size | OS,
        at = list(OS = c(-1, 0, 1)))
```

---

## D. ERP — Nonwords

Again, **separate by time window**.

### D1. N250 — Nonwords

**Question:**
Is early morpho-orthographic parsing sensitive to complexity and family size?

```{r}
erp_nw <- read.csv("erp_dmg_nonwords.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size),
    complexity = factor(complexity),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# ERP nonwords
contrasts(erp_nw$complexity)  <- contr.sum(2)
contrasts(erp_nw$family_size) <- contr.sum(2)

m_nw_N250 <- lmer(
  value ~ complexity*family_size*OS + complexity*family_size*LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
anova(m_nw_N250)
```

---

### D2. N400 — Nonwords (your strongest ERP result)

**Question:**
Does language proficiency determine how familiarity modulates complexity costs?

```{r}
m_nw_N400 <- lmer(
  value ~ complexity*family_size*LP + complexity*family_size*OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_nw_N400)
```

**Critical follow-up:**

```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | LP,
  at = list(LP = c(-1, 0, 1))
)
```
```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | OS,
  at = list(OS = c(-1, 0, 1))
)
```

```{r}
contrast(
  emmeans(m_nw_N400, ~ complexity*family_size | LP,
          at = list(LP = c(-1, 1))),
  interaction = "pairwise"
)
```

---