---
title: "M21_20260502"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```

# WORDS

## RESPONSE TIME DATA

```{r anova_rt_words}

library(lmerTest)

m_rt_words <-lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    (1 | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_rt_words)

# Effect sizes for individual terms
eta_squared(m_rt_words, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_words)
```

## ERP DATA
### N250 DATA
#### Base Frequency

```{r anova_n250_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

m_w_N250_bf <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf)

# Effect sizes for individual terms
eta_squared(m_w_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_bf)
```

#### Family Size

```{r anova_n250_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

m_w_N250_fs <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_fs)

# Effect sizes for individual terms
eta_squared(m_w_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_fs)
```

---

### N400 DATA
#### Base Frequency

```{r anova_N400_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

m_w_N400_bf <- lmer(
  value ~ base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf)

# Effect sizes for individual terms
eta_squared(m_w_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_bf)
```

#### Family Size

```{r anova_N400_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

m_w_N400_fs <- lmer(
  value ~ family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs)

# Effect sizes for individual terms
eta_squared(m_w_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_fs)
```

---

# NON-WORDS
## RESPONSE TIME DATA

```{r anova_rt_nonwords}
contrasts(rt_nw$complexity) <- c(-0.5, 0.5)

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)
m_rt_nw
summary(m_rt_nw)

# Effect sizes for individual terms
eta_squared(m_rt_nw, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_nw)
```

## ERP DATA
### N250 DATA
#### Base Frequency

```{r anova_n250_nonwords_bf}
contrasts(erp_bf_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_bf_nw$base_frequency)  <- c(-0.5, 0.5)

m_nw_N250_bf <- lmer(
  value ~ complexity * OS + complexity * LP + base_frequency +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_bf)

# Effect sizes for individual terms
eta_squared(m_nw_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_bf)
```

#### Family Size

```{r anova_n250_nonwords_fs}
contrasts(erp_fs_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size)  <- c(-0.5, 0.5)

m_nw_N250_fs <- lmer(
  value ~ complexity * OS + complexity * LP + family_size +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_fs)

# Effect sizes for individual terms
eta_squared(m_nw_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_fs)
```

### N400 DATA
#### Base Frequency

```{r anova_n400_nonwords_bf}

contrasts(erp_bf_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_bf_nw$base_frequency) <- c(-0.5, 0.5)

m_nw_N400_bf <- lmer(
  value ~ complexity * base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_bf)


# Effect sizes for individual terms
eta_squared(m_nw_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N400_bf)
```

#### Family Size

```{r anova_n400_nonwords_fs}
contrasts(erp_fs_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400_fs <- lmer(
  value ~ complexity * family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_fs)

# Effect sizes for individual terms
eta_squared(m_nw_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N400_fs)
```



# FOLLOW UP TESTS WORDS
## N250
### Base Frequency
```{r BFxOS_interaction}
# N250 Words: Base Frequency x OS
emm_bf_OS <- emmeans(m_w_N250_bf,
                     ~ base_frequency | OS,
                     at = list(OS = c(-1, 0, 1)))
summary(emm_bf_OS)
pairs(emm_bf_OS)
```

### N400
#### Base Frequency
```{r n400_BFxLP_interaction}
# N400 Words: Base Frequency x LP
emm_bf_LP <- emmeans(m_w_N400_bf,
                     ~ base_frequency | LP,
                     at = list(LP = c(-1, 0, 1)))
summary(emm_bf_LP)
pairs(emm_bf_LP)
```


# FOLLOW UP TESTS  NON-WORDS
## ERP DATA
### N250
#### Base Frequency

```{r n250_CMPxOS_interaction_bf}
# Complexity effect at three levels of OS
emm_complexity_OS_bf <- emmeans(m_nw_N250_bf, 
                              ~ complexity | OS,
                              at = list(OS = c(-1, 0, 1)),pbkrtest.limit = 6480)
summary(emm_complexity_OS_bf)

# Pairwise complexity contrast at each level of OS
pairs(emm_complexity_OS_bf)
```

```{r n250_CMPxLP_interaction_bf}
# Complexity effect at three levels of LP
emm_complexity_LP_bf <- emmeans(m_nw_N250_bf,
                              ~ complexity | LP,
                              at = list(LP = c(-1, 0, 1)),pbkrtest.limit = 6480)
summary(emm_complexity_LP_bf)

# Pairwise complexity contrast at each level of LP
pairs(emm_complexity_LP_bf)
```

#### Family Size
##### Complexity x OS interaction
```{r n250_CMPxOS_interaction_fs}
# Complexity effect at three levels of OS
emm_complexity_OS_fs <- emmeans(m_nw_N250_fs, 
                              ~ complexity | OS,
                              at = list(OS = c(-1, 0, 1)),pbkrtest.limit = 6480)
summary(emm_complexity_OS_fs)

# Pairwise complexity contrast at each level of OS
pairs(emm_complexity_OS_fs)
```

### Complexity × LP Interaction
```{r n250_CMPxLP_interaction_fs}
# Complexity effect at three levels of LP
emm_complexity_LP_fs <- emmeans(m_nw_N250_fs,
                              ~ complexity | LP,
                              at = list(LP = c(-1, 0, 1)), pbkrtest.limit = 6480)
summary(emm_complexity_LP_fs)

# Pairwise complexity contrast at each level of LP
pairs(emm_complexity_LP_fs)
```

### N400
#### Family Size
##### Complexity × Family Size × LP interaction
```{r cmpl_fs_lp_int}
# Step 1: Unpack the three-way
# Complexity x Family Size at three levels of LP
emm_3way <- emmeans(m_nw_N400_fs, 
                    ~ complexity * family_size | LP,
                    at = list(LP = c(-1, 0, 1)), pbkrtest.limit = 6480)
summary(emm_3way)

# Step 2: Pairwise complexity contrasts within each 
# family size condition at each level of LP
pairs(emm_3way, simple = "complexity")

# Step 3: Pairwise family size contrasts within each
# complexity condition at each level of LP
pairs(emm_3way, simple = "family_size")

# Step 4: The interaction contrast — does the complexity x 
# family size interaction itself change across LP levels?
# This is the formal test of the three-way
emm_2way_by_LP <- emmeans(m_nw_N400_fs,
                           ~ complexity * family_size | LP,
                           at = list(LP = c(-1, 0, 1)),pbkrtest.limit = 6480)
contrast(emm_2way_by_LP, 
         interaction = c("pairwise", "pairwise"))
```


#####  Complexity × Family Size interaction averaged across LP

```{r cmpl_fs_int}
# Complexity x Family Size averaged over LP
emm_2way <- emmeans(m_nw_N400_fs, ~ complexity * family_size, pbkrtest.limit = 6480)
summary(emm_2way)
pairs(emm_2way, simple = "complexity")
pairs(emm_2way, simple = "family_size")
```

### Complexity × LP interaction averaged over Family Size:

```{r cmpl_lp_int}
# Complexity x LP averaged over FS at three levels of LP
emm_complexity_LP_N400 <- emmeans(m_nw_N400_fs,
                                   ~ complexity | LP,
                                   at = list(LP = c(-1, 0, 1)), pbkrtest.limit = 6480)
summary(emm_complexity_LP_N400)
pairs(emm_complexity_LP_N400)
```

### FS × LP interaction averaged over Complexity:

```{r}
# Complexity x LP averaged over FS at three levels of LP
emm_FS_LP_N400 <- emmeans(m_nw_N400_fs,
                          ~ family_size | LP,
                          at = list(LP = c(-1, 0, 1)), pbkrtest.limit = 6480)
summary(emm_FS_LP_N400)
pairs(emm_FS_LP_N400)
```

