---
title: "M21_202604"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---


\scriptsize

# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```

1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette_1 <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# set emm options
emm_options(pbkrtest.limit = 4671)

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```

# Load Files

```{r}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("=Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_w <- read_csv("erp_fs_dmg_words.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_nw <- read_csv("erp_fs_dmg_nonwords.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, levels = c("Small", "Large")),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("=Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```

# Response Time (RT)

- **Base Frequency** is your primary lexical familiarity index for **RT models** — it drives the behavioral effects and is interpretable as overall lexical availability. Family Size can be included as a covariate in RT models but should not be foregrounded.

## RT — Words (primary behavioral model)

**Question:**
Does orthographic sensitivity predict efficiency, controlling lexical familiarity?

**Theoretical framing:** RTs index processing speed and overall efficiency. The finding that OS predicts overall RT but does not modulate the structure of morphological effects is theoretically meaningful — it suggests that orthographic skill affects how fast the system operates without changing what it does. This is consistent with discriminative learning accounts in which OS indexes the precision of sublexical cue weights, which would speed all form-based processing rather than selectively facilitating morphologically structured items.

Interactions between morphological variables and individual differences are Question 2 and 3 territory. RT models establish the efficiency baseline cleanly, without prejudging what the ERP models will show.

```{r}
library(lme4)

m_rt_words <- lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    (1 + zLogBF | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_rt_words)
```

- Base Frequency as the primary lexical familiarity predictor
- Family Size included as a covariate but not interacted or foregrounded

**What to report:**

- Main effect of zLogBF — this is your primary finding, should be significant and negative (higher frequency = faster RT). Report and interpret.
- Main effect of zLogFS — this is a covariate. If significant, note it briefly. If not, report the null without dwelling on it.
- Main effect of OS — report whether it reaches significance or shows a trend. This is theoretically meaningful either way: a significant effect supports the efficiency claim; a null effect should be noted honestly.
- Main effect of LP — report as null. One sentence is sufficient.

**What not to report in text:** The random effects structure, the optimizer setting, or any discussion of model convergence unless there was a problem.

**Example narrative pattern:**
Words were recognized more quickly when derived from higher-frequency bases, β = X, SE = X, t(X) = X, p = X. Family size also contributed a reliable facilitory effect, β = X, SE = X, t(X) = X, p = X. Orthographic Sensitivity showed a marginal trend toward faster overall responding, β = X, SE = X, t(X) = X, p = X, whereas Language Proficiency did not reliably predict response times, β = X, SE = X, t(X) = X, p = X.

---

## RT — Nonwords (primary behavioral model)

**Question:**
Does morphological complexity slow decisions, and is this cost modulated by OS?

```{r}

contrasts(rt_nw$complexity) <- c(-0.5, 0.5)

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_rt_nw, ddf = "Kenward-Roger")
```

- Complexity as the primary morphological contrast
- Base Frequency as lexical familiarity covariate

**What to report:**

- Main effect of Complexity — your primary finding, should be large and significant (complex slower than simple). Report and interpret in terms of the processing cost of morphological structure without a stored whole-word representation.
- Main effect of zLogBF — report the inhibitory effect (higher frequency = slower rejection). This is theoretically interesting and worth a sentence of interpretation: high-frequency stems generate strong cue activation that competes with the rejection decision, consistent with discriminative learning accounts.
- Main effect of zLogFS — covariate. Report briefly whether significant or null.
- Main effect of OS — report. If significant, it speaks to overall efficiency for novel forms. If null, note it.
- Main effect of LP — report as null. One sentence.

**What not to report in text:** Again, do not narrate the absence of interactions you did not include — do not say "we did not find a Complexity × OS interaction" because that interaction is not in this model by design. If a reviewer asks, you explain it was a Question 2 test reserved for the ERP.

---

# Early event related potentials (N250)

## ERP — Words

Run **separately by time window** (this is important).

## N250 — Words

**Question:**
Does orthographic sensitivity modulate early sensitivity to morphological family structure?

```{r}
# ERP words

contrasts(family_size) <- c(-0.5, 0.5)

m_w_N250 <- lmer(
  value ~ family_size*OS + family_size*LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_w_N250, ddf = "Kenward-Roger")
```

**Follow-up (only if interaction significant):**

```{r}
library(emmeans)
emmeans(m_w_N250, ~ family_size | OS,
        at = list(OS = c(-1, 0, 1)))
```

---

## C2. N400 — Words

**Question:**
Does language proficiency shape semantic integration of family structure?

```{r}

contrasts(family_size) <- c(-0.5, 0.5)

m_w_N400 <- lmer(
  value ~ family_size*LP + family_size*OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_w_N400)
```

---

# D. ERP — Nonwords

Again, **separate by time window**.

## D1. N250 — Nonwords

**Question:**
Is early morpho-orthographic parsing sensitive to complexity and family size?

```{r}
# ERP nonwords

contrasts(m_nw_N250$complexity) <- c(-0.5, 0.5)
contrasts(m_nw_N250$family_size) <- c(-0.5, 0.5)

m_nw_N250 <- lmer(
  value ~ complexity*family_size*OS + complexity*family_size*LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250)
```

####  Complexity × OS collapsed over Family Size (N250 nonwords)

```{r}
# Confirm factor levels (optional but good)
with(subset(erp_nw, time_window == "N250"), table(complexity, family_size))

# Estimated marginal means of complexity at OS = -1, 0, +1
emm_cx_by_OS <- emmeans(
  m_nw_N250,
  ~ complexity | OS,
  at = list(OS = c(-1, 0, 1)),
  # This is the key: average over family_size
  weights = "proportional"
)
emm_cx_by_OS


# “Slopes”: complexity effect (Complex - Simple) at OS = -1, 0, +1
slopes_cx_OS <- contrast(emm_cx_by_OS, method = "pairwise")  # Complex - Simple within each OS
slopes_cx_OS

# Plot the EMMs (collapsed over family size)
df_emm_OS <- as.data.frame(emm_cx_by_OS)

p_OS <- ggplot(df_emm_OS, aes(x = OS, y = emmean, group = complexity)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.08) +
  labs(
    x = "Orthographic Sensitivity (OS; SD units)",
    y = "Estimated mean N250 amplitude (µV)",
    title = "N250 Nonwords: Complexity effect across OS (averaged over family size)"
  )
p_OS
```

#### Complexity × LP collapsed over Family Size (N250 nonwords)

```{r}
# Estimated marginal means of complexity at LP = -1, 0, +1
emm_cx_by_LP <- emmeans(
  m_nw_N250,
  ~ complexity | LP,
  at = list(LP = c(-1, 0, 1)),
  weights = "proportional"
)
emm_cx_by_LP

# “Slopes”: complexity effect (Complex - Simple) at LP = -1, 0, +1
slopes_cx_LP <- contrast(emm_cx_by_LP, method = "pairwise")  # Complex - Simple within each LP
slopes_cx_LP

# Plot the EMMs (collapsed over family size)
df_emm_LP <- as.data.frame(emm_cx_by_LP)

p_LP <- ggplot(df_emm_LP, aes(x = LP, y = emmean, group = complexity)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.08) +
  labs(
    x = "Language Proficiency (LP; SD units)",
    y = "Estimated mean N250 amplitude (µV)",
    title = "N250 Nonwords: Complexity effect across LP (averaged over family size)"
  )

p_LP
```


---


## D2. N400 — Nonwords (strongest ERP result)

**Question:**
Does language proficiency determine how familiarity modulates complexity costs?

```{r}

contrasts(m_nw_N400$complexity) <- c(-0.5, 0.5)
contrasts(m_nw_N400$family_size) <- c(-0.5, 0.5)

m_nw_N400 <- lmer(
  value ~ complexity*family_size*LP + complexity*family_size*OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_nw_N400)
```

**Critical follow-up:**

```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | LP,
  at = list(LP = c(-1, 0, 1))
)
```
```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | OS,
  at = list(OS = c(-1, 0, 1))
)
```

```{r}
contrast(
  emmeans(m_nw_N400, ~ complexity*family_size | LP,
          at = list(LP = c(-1, 1))),
  interaction = "pairwise"
)
```
#### N400 (nonwords): (Complex - Simple) difference scores as a function of continuous Language Proficiency (LP), averaged over Family Size

.


```{r}
# Generate complexity differences across LP

lp_grid <- seq(-2, 2, by = 0.25)

emm_lp <- emmeans(
  m_nw_N400,
  ~ complexity | LP,
  at = list(LP = lp_grid),
  weights = "proportional"
)

# Compute Complex - Simple difference at each LP
diff_lp <- contrast(emm_lp, method = "pairwise")
df_diff_lp <- as.data.frame(summary(diff_lp, infer = c(TRUE, TRUE)))


# Plot difference scores vs LP
ggplot(df_diff_lp, aes(x = LP, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(size = 1) +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.25
  ) +
  labs(
    x = "Language Proficiency (LP; SD units)",
    y = "N400 Complexity Effect (Complex - Simple, µV)",
    title = "N400 Nonwords: Morphological Complexity Effect as a Function of Language Proficiency",
    subtitle = "Model-estimated difference scores averaged over family size"
  ) +
  theme_classic()

```

---