---
title: "M21_202604"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---


\scriptsize

# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette_1 <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# set emm options
emm_options(pbkrtest.limit = 4671)

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```

# Load Files

```{r load_files}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") %>%
  filter(correct == 1) %>%
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_w <- read_csv("erp_fs_dmg_words.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_nw <- read_csv("erp_fs_dmg_nonwords.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```

# Response Time (RT)

- **Base Frequency** is your primary lexical familiarity index for **RT models** — it drives the behavioral effects and is interpretable as overall lexical availability. Family Size can be included as a covariate in RT models but should not be foregrounded.

## Words — RT

**Question:**
Does orthographic sensitivity predict efficiency, controlling lexical familiarity?

**Theoretical framing:** RTs index processing speed and overall efficiency. The finding that OS predicts overall RT but does not modulate the structure of morphological effects is theoretically meaningful — it suggests that orthographic skill affects how fast the system operates without changing what it does. This is consistent with discriminative learning accounts in which OS indexes the precision of sublexical cue weights, which would speed all form-based processing rather than selectively facilitating morphologically structured items.

RT models: Strip out the morphological structure × individual difference interactions entirely. RTs answer Question 1 only — who is faster — and the models should be specified accordingly. Running leaner models also strengthens the RT results by removing the fragile interaction terms that are currently cluttering them. Interactions between morphological variables and individual differences are Question 2 and 3 territory. RT models establish the efficiency baseline cleanly, without prejudging what the ERP models will show.

```{r anova_rt_words}

library(lmerTest)

m_rt_words <-lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    (1 | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_rt_words)

# Effect sizes for individual terms
eta_squared(m_rt_words, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_words)
```

- Base Frequency as the primary lexical familiarity predictor
- Family Size included as a covariate but not interacted or foregrounded

**What to report:**

- Main effect of zLogBF — this is your primary finding, should be significant and negative (higher frequency = faster RT). Report and interpret.
- Main effect of zLogFS — this is a covariate. If significant, note it briefly. If not, report the null without dwelling on it.
- Main effect of OS — report whether it reaches significance or shows a trend. This is theoretically meaningful either way: a significant effect supports the efficiency claim; a null effect should be noted honestly.
- Main effect of LP — report as null. One sentence is sufficient.

**What not to report in text:** The random effects structure, the optimizer setting, or any discussion of model convergence unless there was a problem.

**Example narrative pattern:**
Words were recognized more quickly when derived from higher-frequency bases, β = X, SE = X, t(X) = X, p = X. Family size also contributed a reliable facilitory effect, β = X, SE = X, t(X) = X, p = X. Orthographic Sensitivity showed a marginal trend toward faster overall responding, β = X, SE = X, t(X) = X, p = X, whereas Language Proficiency did not reliably predict response times, β = X, SE = X, t(X) = X, p = X.

---

## Nonwords — RT

```{r anova_rt_nonwords}
library(lmerTest)

contrasts(rt_nw$complexity) <- c(-0.5, 0.5)

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)
m_rt_nw
summary(m_rt_nw)


# Effect sizes for individual terms
eta_squared(m_rt_nw, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_nw)


```

- Complexity as the primary morphological contrast
- Base Frequency as lexical familiarity covariate

**What to report:**

- Main effect of Complexity — your primary finding, should be large and significant (complex slower than simple). Report and interpret in terms of the processing cost of morphological structure without a stored whole-word representation.
- Main effect of zLogBF — report the inhibitory effect (higher frequency = slower rejection). This is theoretically interesting and worth a sentence of interpretation: high-frequency stems generate strong cue activation that competes with the rejection decision, consistent with discriminative learning accounts.
- Main effect of zLogFS — covariate. Report briefly whether significant or null.
- Main effect of OS — report. If significant, it speaks to overall efficiency for novel forms. If null, note it.
- Main effect of LP — report as null. One sentence.

**What not to report in text:** Again, do not narrate the absence of interactions you did not include — do not say "we did not find a Complexity × OS interaction" because that interaction is not in this model by design. If a reviewer asks, you explain it was a Question 2 test reserved for the ERP.

```{r complexity_maineffect}
library(emmeans)

# Step 1: Get emmeans on log scale with Satterthwaite df
emm_log <- emmeans(m_rt_nw, ~ complexity,lmer.df = "kenward-roger", pbkrtest.limit = 5000)
summary(emm_log)  

# Step 2: Back-transform manually
emm_summary <- summary(emm_log)
emm_summary$mean_ms  <- exp(emm_summary$emmean)
# emm_summary$lower_ms <- exp(emm_summary$asymp.LCL)  # Uncomment for asymptotic df calculation
# emm_summary$upper_ms <- exp(emm_summary$asymp.UCL)
emm_summary$lower_ms <- exp(emm_summary$lower.CL)    # Uncomment for kenward-roger df calculation
emm_summary$upper_ms <- exp(emm_summary$upper.CL)
emm_summary

diff_ms <- exp(emm_summary$emmean[emm_summary$complexity == "Complex"]) - 
           exp(emm_summary$emmean[emm_summary$complexity == "Simple"])
diff_ms
```

---

# Early event related potentials (N250)

Restructure so that OS is the primary moderator and LP is a covariate in the words analysis, while both are tested for nonwords but with OS foregrounded. The three-way Complexity × Family Size × OS interaction for nonwords should be dropped unless you have a specific theoretical reason to retain it — it is currently one of the results that is hardest to interpret and easiest for reviewers to challenge.


## Words — 250 

**Question:**
Does orthographic sensitivity modulate early sensitivity to morphological family structure?

```{r anova_n250_words}
# Set contrast on the data column, not a model object
contrasts(erp_w$family_size) <- c(-0.5, 0.5)

m_w_N250 <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250)

# Effect sizes for individual terms
eta_squared(m_w_N250, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250)
```

**Follow-up (only if interaction significant):**

```{r fs_maineffect}
library(emmeans)
emmeans(m_w_N250, ~ family_size)
```

## Nonwords — N250 

```{r anova_n250_nonwords}
# Set contrasts on data columns before the model
contrasts(erp_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_nw$family_size)  <- c(-0.5, 0.5)

m_nw_N250 <- lmer(
  value ~ complexity * OS + complexity * LP + family_size +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250)

```

### Main Effect of Complexity
Simple means for each level — establishes direction and magnitude:

```{r cmpl_maineffecct}
library(emmeans)
emm_options(lmer.df = "kenward-roger")

emm_complexity <- emmeans(m_nw_N250, ~ complexity)
summary(emm_complexity)
pairs(emm_complexity)
```

### Main Effect of Family Size

```{r fs_maineffect}
emm_fs <- emmeans(m_nw_N250, ~ family_size)
summary(emm_fs)
pairs(emm_fs)
```

### Complexity × OS Interaction
This is your primary Question 2 test. You want to know how the complexity effect changes across levels of OS. The standard approach is to probe OS at −1, 0, and +1 SD:

```{r cmplxos_interaction}
# Complexity effect at three levels of OS
emm_complexity_OS <- emmeans(m_nw_N250, 
                              ~ complexity | OS,
                              at = list(OS = c(-1, 0, 1)))
summary(emm_complexity_OS)

# Pairwise complexity contrast at each level of OS
pairs(emm_complexity_OS)

# Test whether the complexity contrast changes across OS levels
# (this is the formal test of the interaction slope)
# emtrends(m_nw_N250, ~ OS, var = "complexity")
```

### Complexity × LP Interaction. Parallel follow-up for LP:

```{r cmplxls_interaction}
# Complexity effect at three levels of LP
emm_complexity_LP <- emmeans(m_nw_N250,
                              ~ complexity | LP,
                              at = list(LP = c(-1, 0, 1)))
summary(emm_complexity_LP)

# Pairwise complexity contrast at each level of LP
pairs(emm_complexity_LP)

# Formal test of interaction slope
# emtrends(m_nw_N250, ~ LP, var = "complexity1")
```

### Direct Comparison of the Two Interaction Slopes
This is theoretically important — you want to know whether the Complexity × OS and Complexity × LP interactions are meaningfully different from each other, since your theoretical framing predicts both should be present at the N250 but potentially with different magnitudes.

The slopes themselves — $\beta = 0.392$ for OS and $\beta = 0.358$ for LP — are very similar in magnitude, which is consistent with your finding that both dimensions modulate early parsing efficiency for nonwords. Reporting both slopes alongside the follow-up contrasts at ±1 SD will allow you to make this point clearly in the write-up.

```{r interaction_slope_comparison}
# Extract the two slopes
trend_OS <- emtrends(m_nw_N250, ~ OS, var = "complexity1")
trend_LP <- emtrends(m_nw_N250, ~ LP, var = "complexity1")

summary(trend_OS)
summary(trend_LP)
```

#### What to Report From Each

| Test                    | What to report |
|-------------------------|-------------------------------------------------------|
| Complexity main effect  | Means ± CIs for simple and complex, pairwise contrast |
| Family Size main effect | Means ± CIs for large and small, pairwise contrast |
| Complexity × OS         | Complexity contrast at −1, 0, +1 SD of OS; note where effect reverses or disappears |
| Complexity × LP         | Complexity contrast at −1, 0, +1 SD of LP; same logic |
| Slope comparison        | Both emtrends values to show similarity of the two interaction slopes |

The pattern you are looking for in both interactions is the same: at **low skill** the complexity effect should be large and positive (*complex more positive than simple*), at mean skill attenuated, and at **high skill** *reduced or reversed* — consistent with your existing results showing that higher-skill readers show more efficient early parsing of novel morphological structure.

# ERP: N400


**Question:** Does language proficiency shape semantic integration of morphological information (N400)?

Restructure so that LP is the primary moderator and OS is a covariate. The three-way Complexity × Family Size × LP for nonwords is your strongest finding and should be the centerpiece of Question 3 — but it needs to be the planned primary test rather than one of several equally-weighted interactions, which is how it currently reads.

**Theoretical framing**: The N400 indexes semantic integration. The prediction is that LP — which indexes depth and breadth of lexical-semantic knowledge — should modulate the N400 response to morphological family structure, particularly for nonwords where semantic co-activation from family members must be generated from stem-level cues alone. OS is included as a covariate. The key finding is the three-way Complexity × Family Size × LP interaction for nonwords, which is your strongest evidence for the predicted role of LP in morphological family activation during semantic integration.


## N400 — Words


```{r}

contrasts(erp_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400 <- lmer(
  value ~ complexity * family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400)
```

---

##  N400 — Nonwords

**Question:** Does language proficiency determine how familiarity modulates complexity costs?

```{r}

contrasts(erp_nw$complexity) <- c(-0.5, 0.5)
contrasts(erp_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400 <- lmer(
  value ~ complexity*family_size*LP + complexity*family_size*OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_nw_N400)
```

**Critical follow-up:**

```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | LP,
  at = list(LP = c(-1, 0, 1))
)
```
```{r}
emmeans(
  m_nw_N400,
  ~ complexity*family_size | OS,
  at = list(OS = c(-1, 0, 1))
)
```

```{r}
contrast(
  emmeans(m_nw_N400, ~ complexity*family_size | LP,
          at = list(LP = c(-1, 1))),
  interaction = "pairwise"
)
```
#### N400 (nonwords): (Complex - Simple) difference scores as a function of continuous Language Proficiency (LP), averaged over Family Size

.


```{r}
# Generate complexity differences across LP

lp_grid <- seq(-2, 2, by = 0.25)

emm_lp <- emmeans(
  m_nw_N400,
  ~ complexity | LP,
  at = list(LP = lp_grid),
  weights = "proportional"
)

# Compute Complex - Simple difference at each LP
diff_lp <- contrast(emm_lp, method = "pairwise")
df_diff_lp <- as.data.frame(summary(diff_lp, infer = c(TRUE, TRUE)))


# Plot difference scores vs LP
ggplot(df_diff_lp, aes(x = LP, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(size = 1) +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.25
  ) +
  labs(
    x = "Language Proficiency (LP; SD units)",
    y = "N400 Complexity Effect (Complex - Simple, µV)",
    title = "N400 Nonwords: Morphological Complexity Effect as a Function of Language Proficiency",
    subtitle = "Model-estimated difference scores averaged over family size"
  ) +
  theme_classic()

```

---