---
title: "M21_202604"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---


\scriptsize

# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette_1 <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# set emm options
emm_options(pbkrtest.limit = 4671)

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```

# Load Files

```{r load_files}

# Load data: erp_bf words
erp_w <- read_csv("erp_bf_dmg_words.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_nw <- read_csv("erp_bf_dmg_nonwords.csv") %>%
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```

```{r}
names(erp_w)
class(erp_w$base_frequency)
levels(erp_w$base_frequency)
erp_w$base_frequency <- factor(erp_w$base_frequency, 
                                levels = c("Low", "High"))
contrasts(erp_w$base_frequency) <- c(-0.5, 0.5)

# Check variable before running anything

table(erp_w$base_frequency)  # check cell sizes are balanced
```

---

# ERP N250

Restructure so that OS is the primary moderator and LP is a covariate in the words analysis, while both are tested for nonwords but with OS foregrounded. The three-way Complexity × Family Size × OS interaction for nonwords should be dropped unless you have a specific theoretical reason to retain it — it is currently one of the results that is hardest to interpret and easiest for reviewers to challenge.


## Words — 250 

**Question:**
Does orthographic sensitivity modulate early sensitivity to morphological family structure?

```{r anova_n250_words}
# Set contrast on the data column, not a model object
contrasts(erp_w$base_frequency) <- c(-0.5, 0.5)

m_w_N250_bf <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf)

# Effect sizes for individual terms
eta_squared(m_w_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_bf)
```



### Main Effect of Base Frequency

```{r bf_me_n2_wrds}
library(emmeans)
emmeans(m_w_N250_bf, ~ base_frequency)
```

```{r BFxOS_interaction}
# N250 Words: Base Frequency x OS
emm_bf_OS <- emmeans(m_w_N250_bf,
                     ~ base_frequency | OS,
                     at = list(OS = c(-1, 0, 1)))
summary(emm_bf_OS)
pairs(emm_bf_OS)
```

## Nonwords — N250 

```{r anova_n250_nonwords_bf}
contrasts(erp_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_nw$base_frequency)  <- c(-0.5, 0.5)

m_nw_N250_bf <- lmer(
  value ~ complexity * OS + complexity * LP + base_frequency +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_bf)

# Effect sizes for individual terms
eta_squared(m_nw_N250, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_bf)
```

### Main Effect of Complexity
Simple means for each level — establishes direction and magnitude:

```{r cmpl_maineffecct}
library(emmeans)
emm_options(lmer.df = "kenward-roger")

emm_complexity <- emmeans(m_nw_N250, ~ complexity)
summary(emm_complexity)
pairs(emm_complexity)
```

### Main Effect of Family Size

```{r fs_me_n2_nwrd}
emm_fs <- emmeans(m_nw_N250, ~ base_frequency)
summary(emm_fs)
pairs(emm_fs)
```

### Complexity × OS Interaction
This is your primary Question 2 test. You want to know how the complexity effect changes across levels of OS. The standard approach is to probe OS at -1, 0, and +1 SD:

```{r cmplxos_interaction}
# Complexity effect at three levels of OS
emm_complexity_OS <- emmeans(m_nw_N250, 
                              ~ complexity | OS,
                              at = list(OS = c(-1, 0, 1)))
summary(emm_complexity_OS)

# Pairwise complexity contrast at each level of OS
pairs(emm_complexity_OS)

# Test whether the complexity contrast changes across OS levels
# (this is the formal test of the interaction slope)
# emtrends(m_nw_N250, ~ OS, var = "complexity")
```

### Complexity × LP Interaction. Parallel follow-up for LP:

```{r cmplxls_interaction}
# Complexity effect at three levels of LP
emm_complexity_LP <- emmeans(m_nw_N250,
                              ~ complexity | LP,
                              at = list(LP = c(-1, 0, 1)))
summary(emm_complexity_LP)

# Pairwise complexity contrast at each level of LP
pairs(emm_complexity_LP)

# Formal test of interaction slope
# emtrends(m_nw_N250, ~ LP, var = "complexity1")
```

### Complexity Reversal at High OS and LP

```{r n250_nw_complexity_reversal}
library(ggplot2)     # load first, before lmerTest
library(patchwork)   # load second
library(lme4)
library(lmerTest)
library(emmeans)


# --- Set up continuous grids ---
os_grid <- seq(-2, 2, by = 0.25)
lp_grid <- seq(-2, 2, by = 0.25)

# --- OS plot ---
emm_os <- emmeans(
  m_nw_N250,
  ~ complexity | OS,
  at = list(OS = os_grid),
  weights = "proportional"
)

diff_os <- contrast(emm_os, method = "pairwise")
df_os <- as.data.frame(summary(diff_os, infer = c(TRUE, TRUE)))

# --- LP plot ---
emm_lp <- emmeans(
  m_nw_N250,
  ~ complexity | LP,
  at = list(LP = lp_grid),
  weights = "proportional"
)

diff_lp <- contrast(emm_lp, method = "pairwise")
df_lp <- as.data.frame(summary(diff_lp, infer = c(TRUE, TRUE)))

# --- OS plot ---
p_os <- ggplot(df_os, aes(x = OS, y = estimate,
                            ymin = asymp.LCL,
                            ymax = asymp.UCL)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_ribbon(alpha = 0.2, fill = "#2166ac", colour = NA) +
  geom_line(size = 1, colour = "#2166ac") +
  scale_x_continuous(
    breaks = c(-2, -1, 0, 1, 2),
    labels = c("-2 SD", "-1 SD", "Mean", "+1 SD", "+2 SD")
  ) +
  labs(
    x = "Orthographic Sensitivity (SD units)",
    y = "N250 Complexity Effect (Simple \u2212 Complex, \u00b5V)",
    title = "N250 Nonwords: Complexity Effect as a Function of Orthographic Sensitivity",
    subtitle = "Positive values = Simple more negative than Complex\nShaded region shows 95% CI"
  ) +
  theme_classic()

# --- LP plot ---
p_lp <- ggplot(df_lp, aes(x = LP, y = estimate,
                            ymin = asymp.LCL,
                            ymax = asymp.UCL)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_ribbon(alpha = 0.2, fill = "#d6604d", colour = NA) +
  geom_line(size = 1, colour = "#d6604d") +
  scale_x_continuous(
    breaks = c(-2, -1, 0, 1, 2),
    labels = c("-2 SD", "-1 SD", "Mean", "+1 SD", "+2 SD")
  ) +
  labs(
    x = "Language Proficiency (SD units)",
    y = "N250 Complexity Effect (Simple \u2212 Complex, \u00b5V)",
    title = "N250 Nonwords: Complexity Effect as a Function of Language Proficiency",
    subtitle = "Positive values = Simple more negative than Complex\nShaded region shows 95% CI"
  ) +
  theme_classic()

# --- Display separately or combine ---
p_os
p_lp

# Combined figure using patchwork
library(patchwork)
p_os / p_lp +
  plot_annotation(
    title = "N250 Nonwords: Morphological Complexity Effect by Reader Skill",
    subtitle = "Reversal at high skill indicates facilitation by real suffix structure"
  )
```

#### Zero crossing: the point at which the complexity effect disappears. The zero crossing point is theoretically interesting and worth identifying explicitly. 

```{r complexity_reversal_zerocrossingpoint}
# Approximate zero crossing for OS
zero_cross_os <- df_os$OS[which.min(abs(df_os$estimate))]
zero_cross_os

# Approximate zero crossing for LP
zero_cross_lp <- df_lp$LP[which.min(abs(df_lp$estimate))]
zero_cross_lp
```

### Direct Comparison of the Two Interaction Slopes
This is theoretically important — you want to know whether the Complexity × OS and Complexity × LP interactions are meaningfully different from each other, since your theoretical framing predicts both should be present at the N250 but potentially with different magnitudes.

The slopes themselves — $\beta = 0.392$ for OS and $\beta = 0.358$ for LP — are very similar in magnitude, which is consistent with your finding that both dimensions modulate early parsing efficiency for nonwords. Reporting both slopes alongside the follow-up contrasts at ±1 SD will allow you to make this point clearly in the write-up.


#### What to Report From Each

| Test                    | What to report |
|-------------------------|-------------------------------------------------------|
| Complexity main effect  | Means ± CIs for simple and complex, pairwise contrast |
| Family Size main effect | Means ± CIs for large and small, pairwise contrast |
| Complexity × OS         | Complexity contrast at -1, 0, +1 SD of OS; note where effect reverses or disappears |
| Complexity × LP         | Complexity contrast at -1, 0, +1 SD of LP; same logic |
| Slope comparison        | Both emtrends values to show similarity of the two interaction slopes |

The pattern you are looking for in both interactions is the same: at **low skill** the complexity effect should be large and positive (*complex more positive than simple*), at mean skill attenuated, and at **high skill** *reduced or reversed* — consistent with your existing results showing that higher-skill readers show more efficient early parsing of novel morphological structure.

# ERP: N400


**Question:** Does language proficiency shape semantic integration of morphological information (N400)?

Restructure so that LP is the primary moderator and OS is a covariate. The three-way Complexity × Family Size × LP for nonwords is your strongest finding and should be the centerpiece of Question 3 — but it needs to be the planned primary test rather than one of several equally-weighted interactions, which is how it currently reads.

**Theoretical framing**: The N400 indexes semantic integration. The prediction is that LP — which indexes depth and breadth of lexical-semantic knowledge — should modulate the N400 response to morphological family structure, particularly for nonwords where semantic co-activation from family members must be generated from stem-level cues alone. OS is included as a covariate. The key finding is the three-way Complexity × Family Size × LP interaction for nonwords, which is your strongest evidence for the predicted role of LP in morphological family activation during semantic integration.


## N400 — Words


```{r anova_N400_words_bf}
contrasts(erp_w$base_frequency) <- c(-0.5, 0.5)

m_w_N400_bf <- lmer(
  value ~ base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf)

# Effect sizes for individual terms
eta_squared(m_w_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_bf)
```

---

### Main Effect of Base Freqency

```{r fs_me_n4_wrds}
emm_bf_w_N400 <- emmeans(m_w_N400_bf, ~ base_frequency)
summary(emm_bf_w_N400)
pairs(emm_bf_w_N400)
```

```{r n400_BFxLP_interaction}
# N400 Words: Base Frequency x LP
emm_bf_LP <- emmeans(m_w_N400_bf,
                     ~ base_frequency | LP,
                     at = list(LP = c(-1, 0, 1)))
summary(emm_bf_LP)
pairs(emm_bf_LP)
```



##  N400 — Nonwords

**Question:** Does language proficiency determine how familiarity modulates complexity costs?

```{r anova_n400_nonwords_bf}

contrasts(erp_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_nw$base_frequency) <- c(-0.5, 0.5)

m_nw_N400_bf <- lmer(
  value ~ complexity * base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_bf)


# Effect sizes for individual terms
eta_squared(m_nw_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N400_bf)
```

### Complexity × Family Size × LP interaction

The three-way needs to be unpacked by examining the Complexity × Family Size interaction separately at each level of LP. This tells you how the joint influence of morphological complexity and family size on semantic integration changes as a function of language proficiency — which is exactly your theoretical claim.

```{r cmpl_fs_lp_int}
# Step 1: Unpack the three-way
# Complexity x Family Size at three levels of LP
emm_3way <- emmeans(m_nw_N400, 
                    ~ complexity * base_frequency | LP,
                    at = list(LP = c(-1, 0, 1)))
summary(emm_3way)

# Step 2: Pairwise complexity contrasts within each 
# family size condition at each level of LP
pairs(emm_3way, simple = "complexity")

# Step 3: Pairwise family size contrasts within each
# complexity condition at each level of LP
pairs(emm_3way, simple = "base_frequency")

# Step 4: The interaction contrast — does the complexity x 
# family size interaction itself change across LP levels?
# This is the formal test of the three-way
emm_2way_by_LP <- emmeans(m_nw_N400,
                           ~ complexity * base_frequency | LP,
                           at = list(LP = c(-1, 0, 1)))
contrast(emm_2way_by_LP, 
         interaction = c("pairwise", "pairwise"))
```
```{r}
# Generate complexity x family size at three levels of LP
lp_vals <- c(-1, 0, 1)

emm_3way_plot <- emmeans(
  m_nw_N400,
  ~ complexity | base_frequency + LP,
  at = list(LP = lp_vals),
  weights = "proportional"
)

# Compute Simple - Complex within each family size x LP combination
diff_3way <- contrast(emm_3way_plot, 
                      method = "pairwise", 
                      simple = "complexity")
df_3way <- as.data.frame(summary(diff_3way, infer = c(TRUE, TRUE)))

# Add readable labels
df_3way$LP_label <- factor(
  df_3way$LP,
  levels = c(-1, 0, 1),
  labels = c("Low LP (-1 SD)", "Mean LP (0 SD)", "High LP (+1 SD)")
)

df_3way$base_frequency_label <- ifelse(
  df_3way$base_frequency == "Large",
  "Large Family",
  "Small Family"
)

# Plot
ggplot(df_3way, aes(x = LP_label, y = estimate,
                     colour = base_frequency_label,
                     group = base_frequency_label,
                     ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_line(size = 1) +
  geom_point(size = 3) +
  geom_errorbar(width = 0.15, alpha = 0.6) +
  scale_colour_manual(
    values = c("Large Family" = "#2166ac", 
               "Small Family" = "#d6604d"),
    name = "Family Size"
  ) +
  labs(
    x = "Language Proficiency (SD units)",
    y = "N400 Complexity Effect (Simple \u2212 Complex, \u00b5V)",
    title = "N400 Nonwords: Complexity \u00d7 Family Size Interaction by Language Proficiency",
    subtitle = "Model-estimated complexity effects at \u22121, 0, and +1 SD of Language Proficiency"
  ) +
  theme_classic() +
  theme(legend.position = "top")
```

```{r}
# Continuous LP version
lp_vals <- seq(-2, 2, by = 0.25)

emm_3way_plot <- emmeans(
  m_nw_N400,
  ~ complexity | base_frequency + LP,
  at = list(LP = lp_vals),
  weights = "proportional"
)

diff_3way <- contrast(emm_3way_plot,
                      method = "pairwise",
                      simple = "complexity")
df_3way <- as.data.frame(summary(diff_3way, infer = c(TRUE, TRUE)))

# Readable family size labels only — no LP factor conversion
df_3way$base_frequency_label <- ifelse(
  df_3way$base_frequency == "Large",
  "Large Family",
  "Small Family"
)

# Plot with LP as continuous x-axis
ggplot(df_3way, aes(x = LP, y = estimate,
                     colour = base_frequency_label,
                     fill = base_frequency_label,
                     group = base_frequency_label,
                     ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_ribbon(alpha = 0.2, colour = NA) +
  geom_line(size = 1) +
  scale_colour_manual(
    values = c("Large Family" = "#2166ac",
               "Small Family" = "#d6604d"),
    name = "Family Size"
  ) +
  scale_fill_manual(
    values = c("Large Family" = "#2166ac",
               "Small Family" = "#d6604d"),
    name = "Family Size"
  ) +
  scale_x_continuous(
    breaks = c(-2, -1, 0, 1, 2),
    labels = c("-2 SD", "-1 SD", "Mean", "+1 SD", "+2 SD")
  ) +
  labs(
    x = "Language Proficiency (SD units)",
    y = "N400 Complexity Effect (Simple \u2212 Complex, \u00b5V)",
    title = "N400 Nonwords: Complexity \u00d7 Family Size Interaction by Language Proficiency",
    subtitle = "Shaded regions show 95% confidence intervals"
  ) +
  theme_classic() +
  theme(legend.position = "top")
```


###  Complexity × Family Size interaction averaged across LP

```{r cmpl_fs_int}
# Complexity x Family Size averaged over LP
emm_2way <- emmeans(m_nw_N400, ~ complexity * base_frequency)
summary(emm_2way)
pairs(emm_2way, simple = "complexity")
pairs(emm_2way, simple = "base_frequency")
```

```{r}
# Generate complexity x family size interaction plot
# averaged over LP

emm_fs_complexity <- emmeans(
  m_nw_N400,
  ~ complexity | base_frequency,
  weights = "proportional"
)

# Compute Complex - Simple difference within each family size level
diff_fs <- contrast(emm_fs_complexity, method = "pairwise")
df_diff_fs <- as.data.frame(summary(diff_fs, infer = c(TRUE, TRUE)))

# Add readable family size labels
df_diff_fs$base_frequency <- ifelse(
  df_diff_fs$base_frequency == "Large", 
  "Large Family", 
  "Small Family"
)

# Plot
ggplot(df_diff_fs, aes(x = base_frequency, y = estimate, 
                        ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(size = 3) +
  geom_errorbar(width = 0.15) +
  labs(
    x = "Morphological Family Size",
    y = "N400 Complexity Effect (Simple \u2212 Complex, \u00b5V)",
    title = "N400 Nonwords: Complexity Effect by Morphological Family Size",
    subtitle = "Model-estimated difference scores averaged over Language Proficiency"
  ) +
  theme_classic()
```


### Complexity × LP interaction averaged over Family Size:

```{r cmpl_lp_int}
# Complexity x LP averaged over FS at three levels of LP
emm_complexity_LP_N400 <- emmeans(m_nw_N400,
                                   ~ complexity | LP,
                                   at = list(LP = c(-1, 0, 1)))
summary(emm_complexity_LP_N400)
pairs(emm_complexity_LP_N400)
```
```{r}

# Generate complexity differences across LP

lp_grid <- seq(-2, 2, by = 0.25)

emm_lp <- emmeans(
  m_nw_N400,
  ~ complexity | LP,
  at = list(LP = lp_grid),
  weights = "proportional"
)

# Compute Complex - Simple difference at each LP
diff_lp <- contrast(emm_lp, method = "pairwise")
df_diff_lp <- as.data.frame(summary(diff_lp, infer = c(TRUE, TRUE)))


# Plot difference scores vs LP
ggplot(df_diff_lp, aes(x = LP, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(size = 1) +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.25
  ) +
  labs(
    x = "Language Proficiency (LP; SD units)",
    y = "N400 Complexity Effect (Complex - Simple, µV)",
    title = "N400 Nonwords: Morphological Complexity Effect as a Function of Language Proficiency",
    subtitle = "Model-estimated difference scores averaged over family size"
  ) +
  theme_classic()
```
