---
title: "M21 LDT ERP HC ORTHOGRAPIC SENSITIVITY N250 Base Frequency"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Set parameters {-}
Set chunk parameters
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||")
options(width = 140)
```



Load libraries
```{r, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```


Set ggplot parameters
```{r, echo=FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8.5),
                  axis.title=element_text(size=9)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")


# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```

Define standard error of the mean function

```{r, echo=FALSE}
sem <- function(x) sd(x)/sqrt(length(x))
```


# Load data files 

```{r}
dir_path <- "CSV files"

erp_2A <- read_csv(file.path(dir_path, "bf_m21_ldt_mea_200300_050050_1_AB.csv"))
erp_2B <- read_csv(file.path(dir_path, "bf_m21_ldt_mea_200300_050050_1_BA.csv"))

dmg_lng_vsl <- read_csv(file.path(dir_path, "demo_lang_vsl_pca_hc.csv"))
```

```{r}
library(dplyr)

erp_2i <- bind_rows(
  erp_2A |> mutate(List = "AB"),
  erp_2B |> mutate(List = "BA")
)
```

Now we extract `SubjID` from the `ERPset` column
```{r, , echo=FALSE}

# Remove '_LDT_diff_waves' from each string in the ERPset column
# This code first renames the column and then applies the `str_replace` function 
# to the newly renamed column.
erp_2ii <- erp_2i |>
  rename(SubjID = ERPset) |>
  mutate(SubjID = str_replace(SubjID, "_LDT_diff_waves", "")) |>
  mutate(binlabel = str_replace(binlabel, "Critical_", "")) |>
  mutate(binlabel = str_replace(binlabel, "_family", "")) |>
  select(-mlabel)

# erp_4 <- erp_4 |>
#   rename(SubjID = ERPset) |>
#   mutate(SubjID = str_replace(SubjID, "_LDT_diff_waves", "")) |>
#   mutate(binlabel = str_replace(binlabel, "Critical_", "")) |>
#   mutate(binlabel = str_replace(binlabel, "_family", "")) |>
#   select(-mlabel)
```

We then join the ERP data and language into a single data frame
```{r, echo=FALSE}

erp_2iii <- erp_2ii |>
  left_join(dmg_lng_vsl, by = "SubjID") |>
  select(SubjID, everything()) 
# n400 <- erp_4 |>
#   left_join(dmg_lng_vsl, by = "SubjID") |>
#   select(SubjID, everything()) 
```

# Format data files 

Divide into word, non-word and difference wave dataframes
```{r, echo=FALSE}
# n250_words <- erp_2iii |> filter(bini %in% c(1:2))    # does not include BF data
# n250_words_b <- erp_2iii |> filter(bini %in% c(9:12)) # includes BF data
n250_nonwords <- erp_2iii |> filter(bini %in% c(19:22))

```

Then we do some more formatting and cleanup of the dataframes.We  create separate columns, one for each independent variable (anteriority, laterality, morphological family size). To do this we have to use `seperate` function from the `stringr` package. Run `vignette("programming", package = "dplyr")` to see more about `tidy-selection` and `tidy-evaluation`.
<br>  
```{r, echo=FALSE}
# Nonwords
n250_nonwords <- n250_nonwords |>
  separate_wider_delim(
    binlabel,
    delim = "_",
    names = c("Lexicality", "Complexity", "Base_Frequency"),
    too_many = "drop")

# Format as factors
n250_nonwords <- n250_nonwords |>
  mutate(complexity = fct_relevel(Complexity, "Simple", "Complex"))

n250_nonwords <- n250_nonwords |>
  mutate(family_size = fct_relevel(Base_Frequency, "Low", "High"))
```
<br>  
Now we need to  extract just the bins and channels that we intend to analyse. For this analysis we will use 9 channels:  F3, Fz, F4, C3, Cz, C4, P3, Pz, P4 . We will use the`mutate` function from the `dplyr` package along with the `case_when` function. The `case_when` function  is a sequence of two-sided formulas. The left hand side determines which values match this case. The right hand side provides the replacement value.
<br>  
```{r, echo=FALSE}

channels_1 <-  c(3, 2, 25, 7, 20, 21, 12, 11, 16)

# Nonwords
n250_nonwords <- n250_nonwords |>
  filter(chindex %in% channels_1) |> 
  select(-`Included VSL2`)
```
<br>  


# N250 Nonword Data
<br>  
```{r, results='hide'}
n250_nonwords %>%
  count(Base_Frequency, Complexity, Orthographic_Sensitivity)
```


## Compute the ANOVA
<br>  
```{r}
anova_model_n250_nonwords <- mixed(
    value ~ Orthographic_Sensitivity * Base_Frequency * Complexity +
    (1 + Base_Frequency + Complexity | SubjID) +     # by-subject intercept + slopes
    (1 | SubjID:chlabel),                        # electrode nested within subject
  data   = n250_nonwords,
  method = "KR"
)
anova_model_n250_nonwords 

m2 <- anova_model_n250_nonwords$full_model    # Extract the lmer model
ranova(m2)    # Run random effects comparison


# Extract effect sizes from your ANOVA model
eta_squared(anova_model_n250_nonwords, partial = TRUE)

# Compute Marginal(fixed effects only) and Conditional(fixed + random effects) R²
r2(anova_model_n250_nonwords)
```



## Main Effects and Interactions

|                     Effect|        df|      F|       p|Eta2 (partial) | 
|---------------------------|----------|-------|--------|---------------|
|  Base_Frequency:Complexity|1, 4738.00|8.33 **|   .004 |       1.76e-03|


```{r}
# Estimated marginal means for the Base_Frequency x Complexity interaction
(emm2 <- emmeans(anova_model_n250_nonwords, ~ Base_Frequency  * Complexity))

# Get all pairwise contrasts
emm2_contrasts <- contrast(emm2,  method = "pairwise", by = NULL, adjust = "none")
# emm2_contrasts

# Keep only the contrasts you want
# Simple effects of family_size at each level of complexity
# Simple effects of complexity at each level of family_size
keep2 <- c("High Complex - Low Complex",
           "High Simple - Low Simple",
           "High Complex - High Simple",
           "Low Complex - Low Simple")

(emm2_contrasts_filtered <- subset(emm2_contrasts, contrast %in% keep2))

# Get Confidence Intervals
(emm2_contrasts_filtered_ci <- confint(emm2_contrasts_filtered))


# Get effect sizes
# Get all pairwise effect sizes
effs2 <- eff_size(emm2, sigma = sigma(m2), edf = df.residual(m2))

# Remove the  redundant rows 
(effs2_filtered <- subset(effs2, contrast %in% keep2))
```

### Interaction Contrasts
<br>
```{r}
#  Interaction contrasts (difference-of-differences)

contrast(emm2, interaction = "pairwise", by = NULL, adjust = "holm")
confint(contrast(emm2, interaction = c("pairwise", "pairwise")))

# Get confidence intervals, for each base frequency effect for each family size and then for interaction effect
confint(contrast(emmeans(m2, ~ Base_Frequency | Complexity), "pairwise"))
```

## Plots
<br>  
```{r, fig.width=8, fig.height=3.5}
p1 <- emmip(anova_model_n250_nonwords, Base_Frequency  ~ Complexity) + my_style
p2 <- emmip(anova_model_n250_nonwords, Complexity  ~ Base_Frequency) + my_style

plot_grid(p1, p2, ncol = 2)
```






