---
title: "M21 LDT ERP HC SEMANTIC SENSITIVITY N400 Base Frequency"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Set parameters {-}
Set chunk parameters
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||")
options(width = 140)
```



Load libraries
```{r, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```


Set ggplot parameters
```{r, echo=FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8.5),
                  axis.title=element_text(size=9)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")


# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```


Define standard error of the mean function
```{r, echo=FALSE}
sem <- function(x) sd(x)/sqrt(length(x))
```


# Load data files 

```{r}
dir_path <- "CSV files"

erp_4A <- read_csv(file.path(dir_path, "bf_m21_ldt_mea_300500_050050_1_AB.csv"))
erp_4B <- read_csv(file.path(dir_path, "bf_m21_ldt_mea_300500_050050_1_BA.csv"))
dmg_lng_vsl <- read_csv(file.path(dir_path, "demo_lang_vsl_pca_hc.csv"))
```


```{r}
library(dplyr)

erp_4i <- bind_rows(
  erp_4A |> mutate(List = "AB"),
  erp_4B |> mutate(List = "BA")
)
```

Now we extract `SubjID` from the `ERPset` column
```{r, , echo=FALSE}

# Remove '_LDT_diff_waves' from each string in the ERPset column
# This code first renames the column and then applies the `str_replace` function 
# to the newly renamed column.
erp_4ii <- erp_4i |>
  rename(SubjID = ERPset) |>
  mutate(SubjID = str_replace(SubjID, "_LDT_diff_waves", "")) |>
  mutate(binlabel = str_replace(binlabel, "Critical_", "")) |>
  mutate(binlabel = str_replace(binlabel, "_family", "")) |>
  select(-mlabel)

```

We then join the ERP data and language into a single data frame

<br>

```{r, echo=FALSE}
erp_4iii <- erp_4ii |>
  left_join(dmg_lng_vsl, by = "SubjID") |>
  select(SubjID, everything()) 
```

# Format data files 

Divide into word, non-word and difference wave dataframes
```{r, echo=FALSE}

n400_nonwords <- erp_4iii |> filter(bini %in% c(19:22))
```

Then we do some more formatting and cleanup of the dataframes.We  create separate columns, one for each independent variable (anteriority, laterality, morphological family size). To do this we have to use `seperate` function from the `stringr` package. Run `vignette("programming", package = "dplyr")` to see more about `tidy-selection` and `tidy-evaluation`.

```{r, echo=FALSE}
# Nonwords
n400_nonwords <- n400_nonwords |>
  separate_wider_delim(
    binlabel,
    delim = "_",
    names = c("Lexicality", "Complexity", "Base_Frequency"),
    too_many = "drop")

# Format as factors
n400_nonwords <- n400_nonwords |>
  mutate(complexity = fct_relevel(Complexity, "Simple", "Complex"))

n400_nonwords <- n400_nonwords |>
  mutate(family_size = fct_relevel(Base_Frequency, "Low", "High"))
```

Now we need to  extract just the bins and channels that we intend to analyse. For this analysis we will use 9 channels:  F3, Fz, F4, C3, Cz, C4, P3, Pz, P4 . We will use the`mutate` function from the `dplyr` package along with the `case_when` function. The `case_when` function  is a sequence of two-sided formulas. The left hand side determines which values match this case. The right hand side provides the replacement value.

```{r, echo=FALSE}
channels_1 <-  c(3, 2, 25, 7, 20, 21, 12, 11, 16)

# Nonwords
n400_nonwords <- n400_nonwords  |>
  filter(chindex %in% channels_1) |> 
  select(-`Included VSL2`)
```

# N400 Nonword Data

```{r, results='hide'}
n400_nonwords %>%
  count(Base_Frequency, Complexity, Semantic_Sensitivity)
```

## Compute the ANOVA

```{r}
anova_model_n400_nonwords <- mixed(
    value ~ Semantic_Sensitivity * Base_Frequency * Complexity +
    (1 + Base_Frequency + Complexity | SubjID) +     # by-subject intercept + slopes
    (1 | SubjID:chlabel),                        # electrode nested within subject
  data   = n400_nonwords,
  method = "KR"
)
anova_model_n400_nonwords 

m2 <- anova_model_n400_nonwords$full_model    # Extract the lmer model
ranova(m2)    # Run random effects comparison


# Extract effect sizes from your ANOVA model
eta_squared(anova_model_n400_nonwords, partial = TRUE)

# Compute Marginal(fixed effects only) and Conditional(fixed + random effects) R²
r2(anova_model_n400_nonwords)
```
## Main Effects and Interactions

No Main Effects or Interactions