---
title: "M21 LDT ERP HC SEMANTIC SENSITIVITY N250 Family Size"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Set parameters {-}
Set chunk parameters
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||")
options(width = 140)
```



Load libraries
```{r, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```


Set ggplot parameters
```{r, echo=FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8.5),
                  axis.title=element_text(size=9)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")


# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```


Define standard error of the mean function
```{r, echo=FALSE}
sem <- function(x) sd(x)/sqrt(length(x))
```


# Load data files 

```{r}
dir_path <- "CSV files"

erp_2A <- read_csv(file.path(dir_path, "fs_m21_ldt_mea_200300_050050_1_AB.csv"))
erp_2B <- read_csv(file.path(dir_path, "fs_m21_ldt_mea_200300_050050_1_BA.csv"))

dmg_lng_vsl <- read_csv(file.path(dir_path, "demo_lang_vsl_pca_hc.csv"))
```

```{r}
library(dplyr)

erp_2i <- bind_rows(
  erp_2A |> mutate(List = "AB"),
  erp_2B |> mutate(List = "BA")
)
```

Now we extract `SubjID` from the `ERPset` column
```{r, , echo=FALSE}

# Remove '_LDT_diff_waves' from each string in the ERPset column
# This code first renames the column and then applies the `str_replace` function 
# to the newly renamed column.
erp_2ii <- erp_2i |>
  rename(SubjID = ERPset) |>
  mutate(SubjID = str_replace(SubjID, "_LDT_diff_waves", "")) |>
  mutate(binlabel = str_replace(binlabel, "Critical_", "")) |>
  mutate(binlabel = str_replace(binlabel, "_family", "")) |>
  select(-mlabel)

```

We then join the ERP data and language into a single data frame

<br>

```{r, echo=FALSE}
erp_2iii <- erp_2ii |>
  left_join(dmg_lng_vsl, by = "SubjID") |>
  select(SubjID, everything()) 
```

# Format data files 

Divide into word, non-word and difference wave dataframes
```{r, echo=FALSE}
n250_words <- erp_2iii |> filter(bini %in% c(1:2))    # does not include BF data
n250_words_b <- erp_2iii |> filter(bini %in% c(9:12)) # includes BF data
n250_nonwords <- erp_2iii |> filter(bini %in% c(3:6))

```

Then we do some more formatting and cleanup of the dataframes.We  create separate columns, one for each independent variable (anteriority, laterality, morphological family size). To do this we have to use `seperate` function from the `stringr` package. Run `vignette("programming", package = "dplyr")` to see more about `tidy-selection` and `tidy-evaluation`.

```{r, echo=FALSE}
# Words
n250_words <- n250_words |>
  separate(binlabel, into = c("trial_type","family_size"), sep = "_", remove = TRUE) |>
  select(-trial_type)
n250_words_b <- n250_words_b |>
  separate(binlabel, into = c("trial_type", "family_size","tmp1", "base_freq", "tmp2"), sep = "_", remove = TRUE) |>
  select(-c(trial_type, tmp1, tmp2))

n250_words_b$family_size[n250_words_b$family_size == "large"] <- "Large"
n250_words_b$family_size[n250_words_b$family_size == "small"] <- "Small"


# Nonwords
n250_nonwords <- n250_nonwords |>
  separate(binlabel, into = c("trial_type", "family_size", "complexity"), sep = "_", remove = TRUE) |>
  select(-trial_type)

# Assuming your data frame is named 'df' and the column is named 'your_column'
n250_nonwords$complexity[n250_nonwords$complexity == "complex"] <- "Complex"
n250_nonwords$complexity[n250_nonwords$complexity == "simple"] <- "Simple"
n250_nonwords$family_size[n250_nonwords$family_size == "large"] <- "Large"
n250_nonwords$family_size[n250_nonwords$family_size == "small"] <- "Small"

# Format as factors
n250_nonwords <- n250_nonwords |>
  mutate(complexity = fct_relevel(complexity, "Simple", "Complex"))

n250_nonwords <- n250_nonwords |>
  mutate(family_size = fct_relevel(family_size, "Small", "Large"))

# str(n250_nonwords)
```

Now we need to  extract just the bins and channels that we intend to analyse. For this analysis we will use 9 channels:  F3, Fz, F4, C3, Cz, C4, P3, Pz, P4 . We will use the`mutate` function from the `dplyr` package along with the `case_when` function. The `case_when` function  is a sequence of two-sided formulas. The left hand side determines which values match this case. The right hand side provides the replacement value.

```{r, echo=FALSE}

channels_1 <-  c(3, 2, 25, 7, 20, 21, 12, 11, 16)

# Words
n250_words <- n250_words |>
 filter(chindex %in% channels_1) |> 
 select(-`Included VSL2`)

n250_words_b <- n250_words_b |>
  filter(chindex %in% channels_1) |> 
  select(-`Included VSL2`)

# Nonwords
n250_nonwords <- n250_nonwords |>
  filter(chindex %in% channels_1) |> 
  select(-`Included VSL2`)
```


# N250 Word Data

Statistical analysis.

Linear mixed-effects models were fit using the afex::mixed function (method = “KR”) to account for both subject-level and electrode-level variability. Each model included random intercepts for participants (SubjID) and electrodes nested within participants (SubjID:chlabel), as well as by-subject random slopes for within-subject factors ( Family Size, Complexity, or Base Frequency, depending on the analysis). When a significant interaction was obtained, we probed it using estimated marginal means from the fitted model (emmeans package) to clarify the source of the effect.
Because these follow-up contrasts were intended to interpret a significant higher-order interaction rather than to test independent hypotheses, we reported uncorrected p-values (adjust = "none") for interpretive clarity. The robustness of the overall pattern was verified using a Holm correction, which did not change the substantive conclusions.

## Nested ANOVA Model

```{r}
n250_words_b %>%
  count(family_size, base_freq, Semantic_Sensitivity)
```


```{r}
#Fit ANOVA model
anova_model_n250_words_b <- mixed(
    value ~ Semantic_Sensitivity * family_size * base_freq +
    (1 + family_size + base_freq | SubjID) +     # by-subject intercept + slopes
    (1 | SubjID:chlabel),                        # electrode nested within subject
  data   = n250_words_b,
  method = "KR"
)
anova_model_n250_words_b 

m1 <- anova_model_n250_words_b$full_model    # Extract the lmer model
ranova(m1) # Run random effects comparison


# Extract effect sizes from your ANOVA model
eta_squared(anova_model_n250_words_b, partial = TRUE)

# Compute Marginal(fixed effects only) and Conditional(fixed + random effects) R²
r2(anova_model_n250_words_b)
```
## Main Effects

No significant main effects

## Interactions


|                                    Effect|      df|         F| p.value||eta-sqrd|  
|------------------------------------------|--------|----------|--------|---------|
|                     family_size:base_freq| 1, 1498| 32.72 ***|   <.001|    0.02 |
|Semantic_Sensitivity:family_size:base_freq| 1, 1498| 16.96 ***|   <.001|    0.01 |


### `Family Size x Base Frequency` Interaction

<br> 

#### `family_size × base_freq` Simple Contrasts

<br>
```{r}
# Estimated marginal means for the family_size × base frequency interaction
(emm1 <- emmeans(anova_model_n250_words_b, ~ family_size * base_freq))

# Get all pairswise contrasts
emm1_contrasts <- contrast(emm1,  method = "pairwise", by = NULL, adjust = "none")

# Keep only the contrasts you want
# Simple effects of family_size at each level of base_freq
# Simple effects of base_freq at each level of family_size
keep <- c("Large High - Small High",
          "Large Low - Small Low",
          "Large High - Large Low",
          "Small High - Small Low")
(emm1_contrasts_filtered <- subset(emm1_contrasts, contrast %in% keep))

# Get Confidence Intervals
(emm1_contrasts_filtered_ci <- confint(emm1_contrasts_filtered))


# Get effect sizes
# Get all pairwise effect sizes
effs1 <- eff_size(emm1, sigma = sigma(m1), edf = df.residual(m1))

# Remove the two redundant rows (rows 3 and 4)
(effs1_filtered <- subset(effs1, !contrast %in% c("Large High - Small Low",
                                                  "Small High - Large Low")))
```

For large-family words, N250 amplitude is more negative when base frequency is high than when it is low. For small-family words, base frequency has little effect. For low-frequency bases, small-family words elicit more negative amplitudes than large-family words.

- At **High Base Frequency**:  `Large` vs. `Small` family; no difference (-0.0273, *p* = 0.9190). Family size doesn’t matter when base frequency is high.

- At **Low Base Frequency**: `Large` vs. `Small` family; significant difference (0.6634, *p* = 0.0158). When base frequency is low, small-family words yield more negative amplitudes than large-family words

- Within **Small Family**: `High` vs. `Low` base frequency; not significant (0.1812, *p* = 0.4305). Small-family words are unaffected by base frequency.

- Within **Large Family**: High vs. Low base frequency → significant (-0.5095, *p* = 0.0291). Large-family words show more negative amplitudes when their base frequency is high.

<br> 

#### `family_size × base_freq` Interaction Contrasts

<br>

```{r}
#  Interaction contrasts (difference-of-differences)
#    Compare base frequency effect in large vs small family)
contrast(emm1, interaction = "pairwise", by = NULL, adjust = "holm")

# Get confidence intervals, for each base frequency effect for each family size and then for interaction effect
confint(contrast(emmeans(m1, ~ family_size | base_freq), "pairwise"))
confint(contrast(emm1, interaction = c("pairwise", "pairwise")))
```

#### `family_size × base_freq` Interaction Plots
<br>
...

```{r, fig.width = 5.5, fig.height= 3}
p1 <- emmip(anova_model_n250_words_b, family_size ~ base_freq) + my_style
p2 <- emmip(anova_model_n250_words_b, base_freq ~  family_size) + my_style
plot_grid(p1, p2, ncol = 2)
```

### `Sensitivity x Family Size x Base Frequency` Interaction

#### `Sensitivity × family_size × base_freq` Simple Contrasts
<br>
```{r}
# Estimated marginal means for the family_size × base_freq interaction
(emm1b <- emmeans(anova_model_n250_words_b, ~ Semantic_Sensitivity * family_size * base_freq))

# Get all pairswise contrasts
emm1b_contrasts <- contrast(emm1b,  method = "pairwise", by = NULL, adjust = "none")

# Keep only the contrasts you want
# Simple effects of family_size at each level of base_freq
# Simple effects of base_freq at each level of family_size
keep1b <- c("High Semantic Large High - High Semantic Large Low",
          "High Semantic Small High - High Semantic Small Low",
          "Low Semantic Large High - Low Semantic Large Low",
          "Low Semantic Small High - Low Semantic Small Low",
          "High Semantic Large High - High Semantic Small High",
          "High Semantic Large Low - High Semantic Small Low",
          "Low Semantic Large High - Low Semantic Small High",
          "Low Semantic Large Low - Low Semantic Small Low",
          "High Semantic Large High - Low Semantic Large High",
          "High Semantic Small High - Low Semantic Small High",
          "High Semantic Large Low - Low Semantic Small Low",
          "High Semantic Small Low - Low Semantic Small Low")

(emm1b_contrasts_filtered <- subset(emm1b_contrasts, contrast %in% keep1b))

# Get Confidence Intervals
(emm1b_contrasts_filtered_ci <- confint(emm1b_contrasts_filtered))


# Get effect sizes
# Get all pairwise effect sizes
effs1b <- eff_size(emm1b, sigma = sigma(m1), edf = df.residual(m1))

# Remove the  redundant rows 
(effs1b_filtered <- subset(effs1b, contrast %in% keep1b))
```


#### `Sensitivity × family_size × base_freq` Interaction Contrasts

The interaction contrast tests whether the difference in the *base frequency* effect for large vs small families differs across language proficiency?


$$
 [ [(A_1 - A_2)\text{ in }B_1] - [(A_1 - A_2)\text{ in }B_2]
    \text{ in Condition }C_1]
  -
  [[(A_1 - A_2) in B_1] - [(A_1 - A_2) in B_2]
    \text{in Condition }C_2]
$$
<br>
```{r}
#  Interaction contrasts (difference-of-differences)
#    Compare base_freq effect in large vs small family)
contrast(emm1b, interaction = "pairwise", by = NULL, adjust = "holm")
confint(contrast(emm1b, interaction = c("pairwise", "pairwise")))

# Compute the A1 - A2 difference within each combination of B × C
(base_freq_diff <- contrast(emm1b, method = "revpairwise", 
                            by = c("Semantic_sensitivity", "family_size"), 
                            simple = "base_freq"))

# Compute how that A-effect changes across the levels of B, separately for each level of C  
(family_size_base_freq_int_within_sensitivity <- contrast(base_freq_diff, 
                                                           method = "revpairwise",
                                                           by = "Semantic_sensitivity", simple = "family_size"))

# Get confidence intervals
confint(family_size_base_freq_int_within_sensitivity)
```
(a) Base-frequency effect within each Family Size × Sensitivity cell

| Language Proficiency  | Family Size   | Low - High  Base Freq  | *t*   | *p*           |    Interpretation |
|-----------------------|---------------|------------------------|-------|---------------|-------------------|
| High Sensitivity      | Large Family  |  0.7831 µV             | 2.465 |  0.0163       |                   |
| Low Sensitivity       | Large Family  |  0.2358 µV             | 0.718 |  0.4754 (n.s.)|   |
| High Sensitivity      | Small Family  | -0.4049 µV             |-1.274 |  0.2069 (n.s.)|   |
| Low Sensitivity       | Small Family  |  0.0424 µV             | 1.401 |  0.1654 (n.s.)|   |

**Pattern**:
Only high-sensitivity readers show a pronounced base-frequency effect—and only for large-family words; for these large-family words,  where high-frequency bases elicit larger (more negative) N250s.


(b) Difference of those frequency effects across family size (within each group)

| Language Proficiency | (Small – Large Family) $\Delta$ in BF effect | 95% CI           | *p*     | Interpretation |
|----------------------|----------------------------------------------|------------------|---------|----------------|
| High Sensitivity     | –1.188 µV  (-0.4049 - 0.7831)                | [-1.517  -0.859] | <0.0001 | the base-freq effect flips between large- and small-family words. |
| Low Sensitivity      | -0.193 µV  ( 0.0424 - 0.2358)                | [-0.534   0.147] |  0.2655 | No difference in the base frequency effect |


**Interpretation**:

 - High-proficiency participants show a large reversal of the frequency effect between large- and small-family words ($\approx 1.2 \; \mu V$).
 - Low-proficiency participants show none.

#### Plots `Sensitivity × family_size × base_freq`
<br> 
...
```{r, fig.width=8, fig.height=3.5}
p3 <- emmip(anova_model_n250_words_b, family_size ~ base_freq | Semantic_Sensitivity) + my_style
p4 <- emmip(anova_model_n250_words_b, base_freq  ~ family_size |  Semantic_Sensitivity) + my_style
plot_grid(p3, p4, ncol = 2)
```

\newpage

# N250 Nonword Data

```{r, results='hide'}
n250_nonwords %>%
  count(family_size, complexity, Semantic_Sensitivity)
```


## Compute the ANOVA


```{r}
anova_model_n250_nonwords <- mixed(
    value ~ Semantic_Sensitivity * family_size * complexity +
    (1 + family_size + complexity | SubjID) +     # by-subject intercept + slopes
    (1 | SubjID:chlabel),                        # electrode nested within subject
  data   = n250_nonwords,
  method = "KR"
)
anova_model_n250_nonwords 

m2 <- anova_model_n250_nonwords$full_model    # Extract the lmer model
ranova(m2)    # Run random effects comparison


# Extract effect sizes from your ANOVA model
eta_squared(anova_model_n250_nonwords, partial = TRUE)

# Compute Marginal(fixed effects only) and Conditional(fixed + random effects) R²
r2(anova_model_n250_nonwords)
```



## Main Effects and Interactions


|                                     Effect|      df|      F| p.value| eta-sqrd|  
|-------------------------------------------|--------|-------|--------|---------|
|Semantic_Sensitivity:family_size:complexity| 1, 1498| 4.71 *|    .030|3.13e-03 |


###  `Semantic_Sensitivity x family_size x complexity` Simple Contrasts

Compare High vs Low Language Proficiency within each combination of Family Size and Complexity  

This gives you: 4 contrasts: one for each `Family Size × Complexity` combination. Each shows whether `High` vs `Low Language Proficiency` differs significantly

If simple effects aren’t significant, try looking at interaction contrasts, which test differences in the differences. You’re now asking: Does the effect of Sensitivity change more in some complexity/family combinations than others?
<br>
```{r}
# Estimated marginal means for the family_size × complexity interaction
(emm2 <- emmeans(anova_model_n250_nonwords, ~ Semantic_Sensitivity * family_size * complexity))

# Get all pairswise contrasts
emm2_contrasts <- contrast(emm2,  method = "pairwise", by = NULL, adjust = "none")
# emm2_contrasts

# Keep only the contrasts you want
# Simple effects of family_size at each level of complexity
# Simple effects of complexity at each level of family_size
keep2 <- c("High Semantic Large Simple - High Semantic Large Complex",
           "High Semantic Small Simple - High Semantic Small Complex",
           "Low Semantic Large Simple - Low Semantic Large Complex",
           "Low Semantic Small Simple - Low Semantic Small Complex",
           "High Semantic Small Simple - High Semantic Large Simple",
           "High Semantic Small Complex - High Semantic Large Complex",
           "Low Semantic Small Simple - High Semantic Large Simple",
           "Low Semantic Small Complex - Low Semantic Large Complex",
           "High Semantic Large Simple - Low Semantic Large Simple",
           "High Semantic Large Complex - Low Semantic Large Complex",
           "High Semantic Small Simple - Low Semantic Small Simple",
           "High Semantic Small Complex - Low Semantic Small Complex")

(emm2_contrasts_filtered <- subset(emm2_contrasts, contrast %in% keep2))

# Get Confidence Intervals
(emm2_contrasts_filtered_ci <- confint(emm2_contrasts_filtered))


# Get effect sizes
# Get all pairwise effect sizes
effs2 <- eff_size(emm2, sigma = sigma(m2), edf = df.residual(m2))

# Remove the  redundant rows 
(effs2_filtered <- subset(effs2, contrast %in% keep2))
```

###  `Semantic_Sensitivity x family_size x complexity`  Interaction Contrasts

The interaction contrast tests whether the difference in the complexity effect for large vs small families differs across sensitivity?


$$
 [ [(A_1 - A_2)\text{ in }B_1] - [(A_1 - A_2)\text{ in }B_2]
    \text{ in Condition }C_1]
  -
  [[(A_1 - A_2) in B_1] - [(A_1 - A_2)\text{ in }B_2]
    \text{ in Condition }C_2]
$$

<br>
```{r}
#  Interaction contrasts (difference-of-differences)
#    Compare complexity effect in large vs small family)
contrast(emm2, interaction = "pairwise", by = NULL, adjust = "holm")
confint(contrast(emm2, interaction = c("pairwise", "pairwise")))

# Compute the A1 - A2 difference within each combination of B × C
(complexity_diff <- contrast(emm2, method = "revpairwise", 
                            by = c("Semantic_sensitivity", "family_size"), 
                            simple = "complexity"))


# Compute how that A-effect changes across the levels of B, separately for each level of C  
(familysize_complexity_int_within_sensitivity <- contrast(complexity_diff, 
                                                           method = "revpairwise",
                                                           by = "Semantic_sensitivity", simple = "family_size"))

# Get confidence intervals
confint(familysize_complexity_int_within_sensitivity)
```


###  `Semantic_Sensitivity x family_size x complexity`  Plots
<br>  
```{r, fig.width=8, fig.height=3.5}
p5 <- emmip(anova_model_n250_nonwords, family_size ~   complexity| Semantic_Sensitivity)  + my_style
p6 <- emmip(anova_model_n250_nonwords, complexity ~ family_size  | Semantic_Sensitivity)  + my_style
plot_grid(p5, p6, ncol = 2)
```


 - The interaction arises because for high-proficiency participants, there is essentially no difference in N250 amplitude between complex and simple nonwords across either family size.
 - For low-proficiency participants, however, large-family complex nonwords elicit more negative N250s than simple ones, hinting that increased morphological complexity only affects processing when the participant’s language proficiency is low and the item belongs to a large morphological family.


Because these effects were obtained for nonwords in a lexical decision task, we interpret the N250 and N400 modulations as reflecting morpho-orthographic parsing and semantic co-activation from morphemic constituents and morphological families, rather than retrieval of lexical entries. The robust three-way interaction in the N400 indicates that language proficiency alters how family size modulates the semantic co-activation elicited by morphologically complex nonwords—amplifying complexity benefits for low-proficiency readers (especially in large families) but attenuating them for high-proficiency readers, consistent with differences in reliance on semantic co-activation vs. rapid mismatch detection during nonword rejection.