---
title: "M21 RT (Continuous Predictors)"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

\scriptsize

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 4)
options(width = 130)
```

# Setup  {-}

Load libraries
```{r, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
```


1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette)
}

# set emm options
emm_options(pbkrtest.limit = 4671)
```


# Load Files and Format Files  

## Load Files 
```{r}
rt <- read_csv("rt_data_chrt1.csv",  show_col_types = FALSE)
frq_w <- read_csv("frq_cw.csv",  show_col_types = FALSE)
frq_nw <- read_csv("frq_nw.csv",  show_col_types = FALSE)
dmg <- read_csv("demo_lang_vsl_pca_hc.csv", show_col_types = FALSE)
```


## Format Files 
```{r}
# Concatenate datasets

rt_dmg<- right_join(dmg, rt, join_by(SubjID == subject_nr))  # Join Participant Demographic and Lang Data
rt_dmg <- rt_dmg |> mutate(target = tolower(target))
rt_dmg_cor <- rt_dmg |> filter(correct == 1)

# Divide into Experimental and Filler Items
rt_fill <- rt_dmg_cor |> filter(str_detect(targ_type, "^FILL"))
rt_exp <- rt_dmg_cor |> filter(!str_detect(targ_type, "^FILL"))

# Define Factors and Conditions
rt_exp_cln <- rt_exp |>
  separate(targ_type, into = c("trial_type", "family_size", "complexity"), sep = "_",
           remove = TRUE,
           extra = "drop",
           fill = "right")

# Divide into Words and Nonwords
rt_words <- rt_exp_cln |> filter(trial_type == "CW") |> select(- complexity)
rt_nwords <- rt_exp_cln |> filter(trial_type == "NW")

# Join Stimulus Frequency Data
rt_words_frq <- left_join(rt_words, frq_w, join_by(target))|>
  select(-cond_trig.y, -word_trig.y) |>
  rename(cond_trig = cond_trig.x, word_trig = word_trig.x)  # remove duplicate columns

rt_nwords_frq <-  left_join(rt_nwords, frq_nw, join_by(target==word))

# Create a median-split factor for base frequency
rt_words_frq$BF_MedianSplit <- ifelse(
  rt_words_frq$Log10BF <= median(rt_words_frq$Log10BF, na.rm = TRUE),
  "Low", "High")

rt_words_frq$BF_Split <- factor(rt_words_frq$BF_Split)
rt_words_frq$FS_Split <- factor(rt_words_frq$FS_Split)

rt_nwords_frq$BF_Split <- factor(rt_nwords_frq$BF_Split)
rt_nwords_frq$FS_Split <- factor(rt_nwords_frq$FS_Split)
```



## Plot RT  distributions
...

```{r, echo = FALSE, fig.width=7, height = 5.5}
# RT boxplot
p1 <- rt_words_frq |> ggplot(aes(x = SubjID, y = response_time)) +
  geom_boxplot(colour = "#1F78B4", fill = "#1F78B4", alpha = .4 )+
  labs(y = "Respose Time (in milliseconds)", title = "Response Time (Words)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 6, angle = 70, vjust = 0.5, hjust=1))

p2 <- rt_words_frq |> ggplot(aes(x = SubjID, y = response_time)) +
  geom_boxplot(colour = "#E31A1C", fill = "#E31A1C", alpha = .4)+
  labs(y = "Respose Time (in milliseconds)",title = "Response Time (NonWords)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 6, angle = 70, vjust = 0.5, hjust=1))
plot_grid(p1, p2, ncol = 1)

```

## Test for Skewness

`Response Time`

```{r,fig.width=6, fig.height=2 }
# Words Skewness values
skewness(rt_words_frq$response_time, na.rm = TRUE)
skewness(rt_words_frq$LogRT, na.rm = TRUE)

# Words Raw RT Distribution
p1 <- rt_words_frq |> ggplot(aes(x = response_time)) +
  geom_density(colour = "#1F78B4", fill = "#1F78B4", alpha = .4) +
  labs(title = "Raw RT Distribution (Words)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 

# Words Log RT Distribution
p2 <- rt_words_frq |> ggplot(aes(x = InvRT)) +
  geom_density(colour = "#A6CEE3", fill = "#A6CEE3", alpha = .4)  +
  labs(title = "Log RT Distribution (Words)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8))
plot_grid(p1, p2, ncol = 2)


# NONWORDS
# Skewness values
skewness(rt_nwords_frq$response_time, na.rm = TRUE)
skewness(rt_nwords_frq$LogRT, na.rm = TRUE)

# Raw RT
p1 <- rt_nwords_frq |> ggplot(aes(x = response_time)) +
  geom_density(colour = "#E31A1C", fill = "#E31A1C", alpha = .4) +
  labs(y = "Density",title = "Raw RT Distribution (NonWords)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 
# LogRT
p2 <- rt_nwords_frq |> ggplot(aes(x = LogRT)) +
  geom_density(colour = "#FB9A99", fill = "#FB9A99", alpha = .4)  +
  labs(y = "Density", title = "Log RT Distribution (NonWords)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8))
plot_grid(p1, p2, ncol = 2)
```

`Base Frequency`

```{r, echo=FALSE, fig.width=6, fig.height=2}
# WORDS
# Skewness values
skewness(rt_words_frq$BF, na.rm = TRUE)
skewness(rt_words_frq$Log10BF, na.rm = TRUE)

# Raw BF
p1 <- ggplot(rt_words_frq, aes(x = BF)) +
  geom_density(colour = "#B2DF8A", fill = "#B2DF8A", alpha = .4) +
  labs(y = "Density",title = "Raw Base Frequency Distributions (Words)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 
# Log10BF
p2 <- ggplot(rt_words_frq, aes(x = Log10BF)) +
  geom_density(colour = "#33A02C", fill = "#33A02C", alpha = .4) +
  labs(y = "Density",title = "Log10 Base Frequency Distribution (Words)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 
plot_grid(p1, p2, ncol = 2)

# Nonword
# Skewness values
skewness(rt_nwords_frq$BF, na.rm = TRUE)
skewness(rt_nwords_frq$LogBF, na.rm = TRUE)

# Raw BF
p1 <- ggplot(rt_nwords_frq, aes(x = BF)) +
  geom_density(colour = "#B2DF8A", fill = "#B2DF8A", alpha = .4) +
  labs(y = "Density",title = "Raw Base Frequency Distributions (NonWords)") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 

# Log10BF
p2 <- ggplot(rt_nwords_frq, aes(x = LogBF)) +
  geom_density(colour = "#33A02C", fill = "#33A02C", alpha = .4) +
  labs(title = "Log Base Frequency Distribution (NonWords)", y = "Density") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8))
plot_grid(p1, p2, ncol = 2)
```

`Family Size`

```{r, fig.width=6, fig.height=2}
# Words
# Skewness values
rt_words_frq <- rt_words_frq |> mutate(Log10FS = log10(FS))
skewness(rt_words_frq$FS, na.rm = TRUE)
skewness(rt_words_frq$Log10FS, na.rm = TRUE)

# Raw FS 
p1 <- ggplot(rt_words_frq, aes(x = FS)) +
  geom_density(colour = "#A6CEE3", fill = "#1F78B4", alpha = .4) +
  labs(title = "Family Size (Words)", y = "Density") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 
# Log10 FS 
p2 <- ggplot(rt_words_frq, aes(x = Log10FS)) +
  geom_density(colour = "#FB9A99", fill = "#E31A1C", alpha = .4) +
  labs(title = "Log10 Family Size (Words)", y = "Density") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8)) 
plot_grid(p1, p2, ncol = 2)


# NonWords
# Skewness values
rt_nwords_frq <- rt_nwords_frq |> mutate(Log10FS = log10(FS))
skewness(rt_nwords_frq$FS, na.rm = TRUE)
skewness(rt_nwords_frq$Log10FS, na.rm = TRUE)

# Raw FS 
p1 <- ggplot(rt_nwords_frq, aes(x = FS)) +
  geom_density(colour = "#A6CEE3", fill = "#1F78B4", alpha = .4) +
  labs(title = "Family Size (NonWords)", y = "Density") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8))   
# Log10 FS 
p2 <- ggplot(rt_nwords_frq, aes(x = Log10FS)) +
  geom_density(colour = "#FB9A99", fill = "#E31A1C", alpha = .4) +
  labs(title = "Log10 Family Size (NonWords)", y = "Density") +
  theme( plot.title = element_text(size = 9, hjust = .5),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8))  
plot_grid(p1, p2, ncol = 2)

```

# ANOVA Words

Use `complete.cases()` to find which rows had missing data in the model-relevant variables:
```{r, echo=FALSE, results = "hide"}
# Specify only the variables used in the model
model_vars <- c("response_time", "InvRT", "Log10BF","BF", "FS","FS_Split", "Dim.2","SubjID")

# Identify incomplete rows cohort 1
incomplete_cases <- rt_words_frq[!complete.cases(rt_words_frq[, model_vars]), ]
rt_words_cmpl <- rt_words_frq[complete.cases(rt_words_frq[, model_vars]), ]
# View them
# print(incomplete_cases)

# str(rt_words_cmpl)
```


Standardize the predictors
```{r}
rt_words_cmpl$Log10BF_std <- as.numeric(scale(rt_words_cmpl$Log10BF, center = TRUE, scale = TRUE))
rt_words_cmpl$FS_std <- as.numeric(scale(rt_words_cmpl$FS, center = TRUE, scale = TRUE))
rt_words_cmpl$Log10WF_std <- as.numeric(scale(rt_words_cmpl$Log10WF, center = TRUE, scale = TRUE))
rt_words_cmpl$Log10FS_std <- as.numeric(scale(rt_words_cmpl$Log10FS, center = TRUE, scale = TRUE))
rt_words_cmpl$Dim.2_std <- as.numeric(scale(rt_words_cmpl$Dim.2, center = TRUE, scale = TRUE))
```

### Anova with Continuous `Log10BF` and Continuous `Log10FS`

```{r}
# Anova with Continuous Log10BF AND Continous FS
anova_model <- mixed(
  response_time ~ Log10BF_std * Log10FS_std * Orthographic_Sensitivity + (1  | SubjID),
  data = rt_words_cmpl,
  method = "KR"
)
anova_model
summary(anova_model)
eta_squared(anova_model, partial = TRUE)
```

### Effects

|                      Effect|         df |       F |p.value |
|----------------------------|------------|---------|--------|
|                 Log10BF_std| 1, 5792.73 |44.34 ***|   <.001|
|                 Log10FS_std| 1, 5792.42 |31.10 ***|   <.001|
|    Orthographic_Sensitivity| 1,   64.04 | 3.48 +  |    .067|
|Log10BF:FS:Ortho_Sensitivity| 1, 5792.49 |   1.00  |    .317|
	


Main Effect of `Family Size`, `Orthographic Sensitivity`, `Base Frequency`

```{r}
emm_options(pbkrtest.limit = 5864)
emtrends(anova_model, ~1, var = "Log10FS_std")
emtrends(anova_model, ~1, var = "Log10BF_std")

emmeans_obj <- emmeans(anova_model, pairwise ~ Orthographic_Sensitivity)
cohensd_df <- as.data.frame(cohens_d(response_time ~ Orthographic_Sensitivity, data = rt_words_cmpl))
contrasts_df <- as.data.frame(emmeans_obj$contrasts)
(ortho_sens_contrasts <- bind_cols(contrasts_df,cohensd_df))
(ortho_sens_means <-as.data.frame(emmeans_obj$emmeans))



```

`Base Frequency` by `Orthographic Sensitivity` Interaction

```{r}
# estimate simple slopes of base frequency by group:
emtrends(anova_model, ~ Orthographic_Sensitivity, var = "Log10BF_std")
emtrends(anova_model, pairwise ~ Orthographic_Sensitivity, var = "Log10BF_std")

# Estimate marginal means of RT at the mean of both predictors
emm <- emmeans(anova_model, ~ Orthographic_Sensitivity, at = list(Log10BF_std = 0, Log10FS_std = 0))
emm_df <- as.data.frame(emm)

print(emm_df)
```


### Plots

`Family Size` x `Base Frequency` x `Orthographic Sensitivity`

```{r, fig.width=7}
# re-run anova with lmer to use `ggeffects`
anova_model_lmer <- lmer(response_time ~ Log10BF_std * Log10FS_std * Orthographic_Sensitivity + (1 | SubjID), data = rt_words_cmpl)
# Generate predicted values
preds <- ggpredict(anova_model_lmer, terms = c("Log10BF_std", "Orthographic_Sensitivity", "Log10FS_std [-2,0,2]"))

# Plot
ggplot(preds, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  facet_wrap(~facet, labeller = label_value) +
  labs(x = "Standardized Base Frequency (Log10 BF)",
       y = "Predicted  RT",
       color = "Family Size (Log10 FS)",
       fill = "Family Size (Log10 FS)",
       title = "Predicted  RT by Base Frequency, Family Size, and Orthographic Sensitivity")+
  theme( plot.title = element_text(size = 8, hjust = .5),
         legend.title = element_blank(),
         axis.text.x = element_text(size = 8))   
```


# ANOVA Non-Words

Use `complete.cases()` to find which rows had missing data in the model-relevant variables:
```{r, echo=FALSE, results = "hide"}
# Specify only the variables used in the model
model_vars <- c("response_time", "InvRT", "Dim.2","SubjID")

# Identify incomplete rows cohort 1
incomplete_cases <- rt_nwords_frq[!complete.cases(rt_nwords_frq[, model_vars]), ]
rt_nwords_cmpl <- rt_nwords_frq[complete.cases(rt_nwords_frq[, model_vars]), ]
# View them
# print(incomplete_cases)

# str(rt_nwords_cmpl)
```

Standardize the predictors

```{r}

rt_nwords_cmpl$Log10BF_std <- as.numeric(scale(rt_nwords_cmpl$Log10BF, center = TRUE, scale = TRUE))
rt_nwords_cmpl$FS_std <- as.numeric(scale(rt_nwords_cmpl$FS, center = TRUE, scale = TRUE))
rt_nwords_cmpl$Log10FS_std <- as.numeric(scale(rt_nwords_cmpl$Log10FS, center = TRUE, scale = TRUE))
rt_nwords_cmpl$BF_std <- as.numeric(scale(rt_nwords_cmpl$BF, center = TRUE, scale = TRUE))
rt_nwords_cmpl$Dim.2_std <- as.numeric(scale(rt_nwords_cmpl$Dim.2, center = TRUE, scale = TRUE))
rt_nwords_cmpl <- rt_nwords_cmpl |>  select(-complexity.x)
rt_nwords_cmpl <- rename(rt_nwords_cmpl, complexity = complexity.y)
```


Test Correlation between `Base Frequency` and `Complexity`

```{r}
t.test(Log10BF ~ complexity, data = rt_nwords_cmpl)

# Create a contingency table
table_data <- table(rt_nwords_cmpl$complexity, rt_nwords_cmpl$BF_Split)

# Run the chi-square test
chisq.test(table_data)
```


### Anova with Continuous `Log10BF` and Categorical `Complexity`

```{r}

anova_model_2 <- mixed(
  response_time ~ complexity * Log10FS_std * Orthographic_Sensitivity + (1  | SubjID),
  data = rt_nwords_cmpl,
  method = "KR"
)
anova_model_2
summary(anova_model_2)
```


### Effects

|                     Effect|         df |       F    |p.value  |
|---------------------------|------------|------------|---------|
|                 complexity|  1, 4600.75| 106.13 *** |  <.001  |
|   Orthographic_Sensitivity|  1,   64.11|   5.32 *   |   .024  |
|     complexity:Log10FS_std|  1, 4600.65|   3.96 *   |   .047  |



```{r}
# Complexity
emmeans_obj <- emmeans(anova_model_2, pairwise ~ complexity)
cohensd_df <- as.data.frame(cohens_d(response_time ~ complexity, data = rt_nwords_cmpl))
contrasts_df <- as.data.frame(emmeans_obj$contrasts)
(complexity_df <- bind_cols(contrasts_df,cohensd_df))
(complexity_means <-as.data.frame(emmeans_obj$emmeans))

# Orthographic_Sensitivity
emmeans_obj <- emmeans(anova_model_2, pairwise ~ Orthographic_Sensitivity)
cohensd_df <- as.data.frame(cohens_d(response_time ~ Orthographic_Sensitivity, data = rt_nwords_cmpl))
contrasts_df <- as.data.frame(emmeans_obj$contrasts)
(ortho_sens_df <- bind_cols(contrasts_df,cohensd_df))
(ortho_sens_means <-as.data.frame(emmeans_obj$emmeans))

```


```{r}
# Estimate the effect of complexity at low, mean, and high FS
em_complexity <- emmeans(anova_model_2, ~ complexity | Log10FS_std, at = list(Log10FS_std = c(-1, 0, 1)))
summary(em_complexity)

# Estimate the slope of Log10FS within each complexity level
em_trends <- emtrends(anova_model_2, ~ complexity, var = "Log10FS_std")
summary(em_trends)

```


### Plots
...

```{r, fig.height=3.5, fig.width=3.5}
# Plot

# Refit the model using lmer()
anova_model_lmer <- lmer(
  response_time ~ complexity * Log10FS_std * Orthographic_Sensitivity + (1 | SubjID),
  data = rt_nwords_cmpl,
  REML = FALSE
)

# Get predicted values
preds <- ggpredict(anova_model_lmer, terms = c("Log10FS_std", "complexity"))

# Plot
ggplot(preds, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  labs(x = "Standardized Log Family Size",
       y = "Predicted RT (ms)",
       color = "Complexity",
       fill = "Complexity",
       title = "Interaction of Morphological Complexity and Family Size on RT") +
  theme( plot.title = element_text(size = 8, hjust = .5),
         legend.title = element_blank(),
         axis.text.x = element_text(size = 8))   

```



