---
title: "Morph 21"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error = FALSE)
```

This R script contains the code for analysing the morph 21 erp data for the 200-300 ms time window.

1. First we load the libraries we need

```{r}
library(readr)
library(psych)
library(dplyr)
library(tidyr)
```

2. Then we read in the demographic data file
```{r}
m21_dem <- read_csv("csv_files/m21_dem_data.csv")
```


3. ...and the N250 erp data file
```{r}
m21_n250 <- read_csv("csv_files/S101-177_n250.csv")
```

4. Then we join the demographic and erp data files. We will use the `inner_join` rather than the `full_join` function in order to eliminate rows with missing data.

```{r}
m21_n250 <- inner_join(m21_dem,m21_n250, by = "SubjID")
```


5. Let's save a `.csv` file with the data from the combined dataset 

```{r}
write_csv(m21_n250, "csv_files/m21_dem_erp_n250_rmna.csv")
```


6. For each dataset, we will create a subset with only the electrode sites we will be 
analysing—F3, Fz, F4, C3, Cz, C4, P3, Pz, P4

```{r}
sites = c(3,2, 25, 7, 20, 21, 12, 11, 16)
m21_n250_9 <- dplyr::filter(m21_n250, chindex %in% sites)

```


7. We then create separate columns, one for each independent variable (anteriority, laterality, morphological family size). To do this we have to use the`mutate` function from the dplyr package along with the `case_when` function. The `case_when` function  is a sequence of two-sided formulas. The left hand side determines which values match this case. The right hand side provides the replacement value.

```{r}
m21_n250_9 <- dplyr::mutate(m21_n250_9,
                            anteriority = case_when(grepl("F", chlabel) ~ "Frontal",
                                              grepl("C", chlabel) ~ "Central",
                                              grepl("P", chlabel) ~ "Parietal"
                                              )
                            )

m21_n250_9 <- dplyr::mutate(m21_n250_9, 
                            laterality = case_when(grepl("3", chlabel) ~ "Left",
                                                    grepl("z", chlabel) ~ "Midline",
                                                    grepl("Z", chlabel) ~ "Midline",
                                                    grepl("4", chlabel) ~ "Right"
                            )
)



m21_n250_9 <- dplyr::mutate(m21_n250_9, 
                            fam_size = case_when(grepl("small", binlabel) ~ "Small",
                                                   grepl("large", binlabel) ~ "Large"
                            )
)
```


8. We then create a smaller dataset with only the columns we need

```{r}
m21_n250_9b <- dplyr::select(m21_n250_9, 
                             SubjID, 
                             Type, 
                             anteriority, 
                             laterality, 
                             fam_size,
                             value,
                             chlabel,
                             binlabel)
```

9. We then divide dataset into 3 separate ones—for "words", "simple nonwords" and "complex nonwords"

```{r}
m21_n250_words <- dplyr::filter(m21_n250_9b, grepl("Critical_word",binlabel))
m21_n250_nwsmpl <- dplyr::filter(m21_n250_9b, grepl("simple",binlabel))
m21_n250_nwcplx <- dplyr::filter(m21_n250_9b, grepl("complex",binlabel))
```

10. Now we can compute the ANOVA for each of the three datasets.

We use the `aov` function to calculate the source table and F. But before we do that, we want to tell R to change the way it is comparing the groups. We are going to use `Helmert` contrast, and we only need to set it once for all ANOVAs we run during a single R session. 


```{r set_anova_options}
options(contrasts = c("contr.helmert", "contr.poly")) 
options("contrasts")
```

After we tell R we want to use a Helmert contrast (`contr. helmert`) for categorical variables (and polynomial contrasts for ordered variables (`contr.poly`)), we can now run our ANOVA. For more on contrasts see [this explanation](https://stats.libretexts.org/Bookshelves/Applied_Statistics/Book%3A_Learning_Statistics_with_R_-_A_tutorial_for_Psychology_Students_and_other_Beginners_(Navarro)/16%3A_Factorial_ANOVA/16.07%3A_Different_Ways_to_Specify_Contrasts)


```{r runAnova}
m1 <- aov(value ~ Type * fam_size * anteriority * laterality, data = m21_n250_words)
m2 <- aov(value ~ Type * fam_size * anteriority * laterality, data = m21_n250_nwsmpl)
m3 <- aov(value ~ Type * fam_size * anteriority * laterality, data = m21_n250_nwcplx)
summary(m1)
summary(m2)
summary(m3)
```

We can also use the function `Anova()` from the `car` package with the argument `type = III` to get the source table. For our design with no factors with more than 2 levels, both methods should give similar results.  For more on types of sums of square see [this explanation](https://stats.libretexts.org/Bookshelves/Applied_Statistics/Book%3A_Learning_Statistics_with_R_-_A_tutorial_for_Psychology_Students_and_other_Beginners_(Navarro)/16%3A_Factorial_ANOVA/16.10%3A_Factorial_ANOVA_3-_Unbalanced_Designs)

```{r sourceTable}
library(car)
Anova(m1, type = "III")
Anova(m2, type = "III")
Anova(m3, type = "III")
```

#Plot Means

Create an interaction plot for all four groups. For this first example of an interaction plot, we are using as many of the default options as possible. So, we just need to tell the function what variable to use for the x-axis (`x.factor`), what variable to use for the y-axis (`response`), and what variable to use for each line (`trace.factor`) along with what type of number we are plotting. By default, interaction.plot will plot the means of each group

```{r interactionPlot}

interaction.plot(x.factor = m21_n250_words$Type, 
                 trace.factor = m21_n250_words$fam_size, 
                 response = m21_n250_words$value, 
                 xlab = "Participant Type", 
                 ylab = "Mean amplitude of N250 in microvolts", 
                 trace.label = "Morphological Family Size", 
                 col = c('darkred', 'cadetblue'), 
                 type='o',
                 pch=19,
                 lwd=2.5,
                 cex=1.5,
                 legend = FALSE,
                 fixed = TRUE)
 legend("topleft", c("Large","Small"), lwd = 3, col = c('darkred', 'cadetblue'), lty = c(2,1))

interaction.plot(x.factor = m21_n250_words$Type, trace.factor = m21_n250_words$fam_size, response = m21_n250_words$value, xlab = "Participant Type", ylab = "Mean amplitude of N250 in microvolts", trace.label = "Morphological Family Size", col = c('darkred', 'cadetblue'),pch=19,lwd=2.5,cex=1.5,legend = TRUE, xpd = TRUE, fixed = TRUE)

interaction.plot(x.factor = m21_n250_nwsmpl$Type, 
                 trace.factor = m21_n250_nwsmpl$fam_size, 
                 response = m21_n250_nwsmpl$value, 
                 xlab = "Participant Type", 
                 ylab = "Mean amplitude of N250 in microvolts", 
                 trace.label = "Morphological Family Size", 
                 col = c('tomato3', 'steelblue1'), 
                 type='o',
                 pch=19,
                 lwd=2.5,
                 cex=1.5, 
                 legend = FALSE,
                 fixed = TRUE)
legend("left", c("Large","Small"), lwd = 3, col = c('tomato3', 'steelblue1'), lty = c(2,1))

interaction.plot(x.factor = m21_n250_nwsmpl$Type, trace.factor = m21_n250_nwsmpl$fam_size, response = m21_n250_nwsmpl$value, xlab = "Participant Type", ylab = "Mean amplitude of N250 in microvolts", trace.label = "Morphological Family Size", col = c('tomato3', 'steelblue1'), pch=19,lwd=2.5,cex=1.5,legend = TRUE, xpd = TRUE, fixed = TRUE)

interaction.plot(x.factor = m21_n250_nwcplx$Type, trace.factor = m21_n250_nwcplx$fam_size, response = m21_n250_nwcplx$value, xlab = "Participant Type", ylab = "Mean amplitude of N250 in microvolts", trace.label = "Morphological Family Size", col = c('firebrick1', 'dodgerblue'), type='o',pch=19,lwd=2.5,cex=1.5, legend = TRUE, xpd = TRUE, fixed = TRUE)

interaction.plot(x.factor = m21_n250_nwcplx$Type, trace.factor = m21_n250_nwcplx$fam_size, response = m21_n250_nwcplx$value, xlab = "Participant Type", ylab = "Mean amplitude of N250 in microvolts", trace.label = "Morphological Family Size", col = c('firebrick1', 'dodgerblue'),pch=19,lwd=2.5,cex=1.5,legend = TRUE, xpd = TRUE, fixed = TRUE)
```

