---
title: "M21 RT (Continuous Predictors)"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---


\scriptsize
# Setup  {-}
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```


Load libraries
```{r load_libraries, echo=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(emmeans)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
```


1. Set `ggplot2` parameters
```{r theme, echo = FALSE}
theme_set(theme_classic() +  
            theme(legend.position = "bottom", 
                  axis.text=element_text(size=8),
                  axis.title=element_text(size=9),
                  plot.title = element_text(size = 9),
                  plot.subtitle = element_text(size = 8)))

my_theme <- theme(strip.text = element_text(size = 7),
                  axis.text.x = element_text(size = 7),
                  legend.text = element_text(size = 6),
                  legend.title = element_blank())

# Define a custom color palette
my_palette <- c("#1F78B4","#E31A1C", "#33A02C")
my_palette_1 <- c("#A6CEE3",  "#FB9A99")
my_palette_2 <- c( "#1F78B4","#E31A1C" )
my_palette_3 <- c("#A6CEE3","#1F78B4","#FB9A99","#E31A1C")

# Create a function to apply this palette
scale_color_custom <- function() {
  scale_color_manual(values = my_palette_2)
}

scale_fill_custom <- function() {
  scale_fill_manual(values = my_palette_2)
}

# set emm options
emm_options(pbkrtest.limit = 4671)

# Combine theme and scales
my_style <- list(my_theme,scale_color_custom(),scale_fill_custom())
```


# Load Files and Format Files  {-}

## Load Files 

```{r load_files}
#DIR <- "csv_files"
df_a <- read_csv("rt_data_hc_A.csv")
df_b <- read_csv( "rt_data_hc_B_fixed.csv")
frq_w <- read_csv("frq_cw.csv")
frq_nw <- read_csv("frq_nw.csv")
dmg <- read_csv("demo_lang_vsl_pca_hc.csv")
```


## Format Files 

```{r format_files}
# Concatenate datasets
rt <- bind_rows(AB = df_a, 
                BA = df_b,
               .id = "List")
rt_dmg<- right_join(dmg, rt, join_by(SubjID == subject_nr)) |>  # Join Participant Demographic and Lang Data
                    mutate(target = tolower(target)) |>
                    filter(correct == 1)

# Divide into Experimental and Filler Items
rt_fill <- rt_dmg |> filter(str_detect(targ_type, "^FILL"))
rt_exp <- rt_dmg |> filter(!str_detect(targ_type, "^FILL"))

# Add logFS to frequency datasets
frq_w <- frq_w |> mutate(Log10FS = log10(FS))
frq_nw <- frq_nw |> mutate(Log10FS = log10(FS))

# Define Factors and Conditions
rt_exp_format <- rt_exp |>
  separate(targ_type, into = c("trial_type", "family_size", "complexity"), sep = "_",
           remove = TRUE,
           extra = "drop",
           fill = "right")

# Divide into Words and Nonwords
rt_words <- rt_exp_format |> filter(trial_type == "CW") |> select(- complexity)
rt_nwords <- rt_exp_format |> filter(trial_type == "NW")

# Join Stimulus Frequency Data
rt_words_frq <- left_join(rt_words, frq_w, join_by(target))|>
  select(-cond_trig.y, -word_trig.y) |>
  rename(cond_trig = cond_trig.x, word_trig = word_trig.x)  # remove duplicate columns
rt_nwords_frq <-  left_join(rt_nwords, frq_nw, join_by(target==word)) |>   
  select(-cond_trig.y, -word_trig.y) |>
  rename(cond_trig = cond_trig.x, word_trig = word_trig.x)  

# Rename BF_Split and FS_Split columns
rt_words_frq <- rt_words_frq |> rename(Base_Frequency = BF_Split, Family_Size = FS_Split) # Rename BF_Split and FS_Split columns
rt_nwords_frq <- rt_nwords_frq |> rename(Base_Frequency = BF_Split, Family_Size = FS_Split)

# Recode factor levels
# rt_words_frq <- rt_words_frq |>
#   mutate(Base_Frequency = case_match(Base_Frequency, "Low" ~ "Low BF", "High" ~ "High BF"),
#          Family_Size = case_match(Family_Size, "Small" ~ "Small Family", "Large" ~ "Large Family"))
# rt_nwords_frq <- rt_nwords_frq |> mutate(Base_Frequency = case_match(Base_Frequency, "Low" ~ "Low BF", "High" ~ "High BF"),
#                                          Family_Size = case_match(Family_Size, "Small" ~ "Small Family", "Large" ~ "Large Family"))
# 
# rt_words_frq$Orthographic_Sensitivity[rt_words_frq$Orthographic_Sensitivity == "Low"] <- "Low Sensitivity"
# rt_words_frq$Orthographic_Sensitivity[rt_words_frq$Orthographic_Sensitivity == "High"] <- "High Sensitivity"
```



# Word Data

Use `complete.cases()` to find which rows have missing data in the model-relevant variables:

```{r remove_NA_words}
# Specify only the variables used in the model
model_vars_w <- c("response_time",  "Log10BF","BF", "FS","Family_Size", "Base_Frequency", "Orthographic_Sensitivity","Semantic_Sensitivity","Dim.1", "Dim.2","SubjID")

# Identify incomplete rows cohort 1
incomplete_cases_words <- rt_words_frq[!complete.cases(rt_words_frq[, model_vars_w]), ]
rt_words_cmpl <- rt_words_frq[complete.cases(rt_words_frq[, model_vars_w]), ]
# View them
# print(incomplete_cases_words)

```

Standardize the predictors
```{r standardize_predictors_words}
rt_words_cmpl$Log10BF_std <- as.numeric(scale(rt_words_cmpl$Log10BF, center = TRUE, scale = TRUE))
rt_words_cmpl$FS_std <- as.numeric(scale(rt_words_cmpl$FS, center = TRUE, scale = TRUE))
rt_words_cmpl$Log10WF_std <- as.numeric(scale(rt_words_cmpl$Log10WF, center = TRUE, scale = TRUE))
rt_words_cmpl$Log10FS_std <- as.numeric(scale(rt_words_cmpl$Log10FS, center = TRUE, scale = TRUE))
rt_words_cmpl$Dim.2_std <- as.numeric(scale(rt_words_cmpl$Dim.2, center = TRUE, scale = TRUE))
```

### Anova with Continuous `Log10BF` and Continuous `Log10FS`

```{r anova_cntBF_cntFS}
# Anova with Continuous Log10BF AND Continous FS
anova_model <- mixed(
  response_time ~ Log10BF_std * Log10FS_std * Orthographic_Sensitivity + (1  | SubjID),
  data = rt_words_cmpl,
  method = "KR"
)
anova_model
summary(anova_model)
eta_squared(anova_model, partial = TRUE)
```

### Effects

|                      Effect|         df |       F |p.value |
|----------------------------|------------|---------|--------|
|                 Log10BF_std| 1, 5792.73 |44.34 ***|   <.001|
|                 Log10FS_std| 1, 5792.42 |31.10 ***|   <.001|
|    Orthographic_Sensitivity| 1,   64.04 | 3.48 +  |    .067|
|Log10BF:FS:Ortho_Sensitivity| 1, 5792.49 |   1.00  |    .317|
	


```{r anova_cntBF_cntFS_cntDim2}
# Anova with Continuous Log10BF AND Continous FS
anova_model <- mixed(
  response_time ~ Log10BF_std * Log10FS_std * Dim.2 + (1  | SubjID),
  data = rt_words_cmpl,
  method = "KR"
)
anova_model
summary(anova_model)
eta_squared(anova_model, partial = TRUE)
```
### Effects

|                      Effect|         df |       F |p.value |
|----------------------------|------------|---------|--------|
|                 Log10BF_std| 1, 5774.74 |44.34 ***|   <.001|
|                 Log10FS_std| 1, 5792.42 |31.10 ***|   <.001|
|    Orthographic_Sensitivity| 1,   64.04 | 3.48 +  |    .067|
|Log10BF:FS:Ortho_Sensitivity| 1, 5792.49 |   1.00  |    .317|


Main Effect of `Family Size`, `Orthographic Sensitivity`, `Base Frequency`

```{r}
emm_options(pbkrtest.limit = 5864)
emtrends(anova_model, ~1, var = "Log10FS_std")
emtrends(anova_model, ~1, var = "Log10BF_std")

emmeans_obj <- emmeans(anova_model, pairwise ~ Orthographic_Sensitivity)
cohensd_df <- as.data.frame(cohens_d(response_time ~ Orthographic_Sensitivity, data = rt_words_cmpl))
contrasts_df <- as.data.frame(emmeans_obj$contrasts)
(ortho_sens_contrasts <- bind_cols(contrasts_df,cohensd_df))
(ortho_sens_means <-as.data.frame(emmeans_obj$emmeans))



```

`Base Frequency` by `Orthographic Sensitivity` Interaction

```{r}
# estimate simple slopes of base frequency by group:
emtrends(anova_model, ~ Orthographic_Sensitivity, var = "Log10BF_std")
emtrends(anova_model, pairwise ~ Orthographic_Sensitivity, var = "Log10BF_std")

# Estimate marginal means of RT at the mean of both predictors
emm <- emmeans(anova_model, ~ Orthographic_Sensitivity, at = list(Log10BF_std = 0, Log10FS_std = 0))
emm_df <- as.data.frame(emm)

print(emm_df)
```


### Plots

`Family Size` x `Base Frequency` x `Orthographic Sensitivity`

```{r, fig.width=7}
# re-run anova with lmer to use `ggeffects`
anova_model_lmer <- lmer(response_time ~ Log10BF_std * Log10FS_std * Orthographic_Sensitivity + (1 | SubjID), data = rt_words_cmpl)
# Generate predicted values
preds <- ggpredict(anova_model_lmer, terms = c("Log10BF_std", "Orthographic_Sensitivity", "Log10FS_std [-2,0,2]"))

# Plot
ggplot(preds, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  facet_wrap(~facet, labeller = label_value) +
  labs(x = "Standardized Base Frequency (Log10 BF)",
       y = "Predicted  RT",
       color = "Family Size (Log10 FS)",
       fill = "Family Size (Log10 FS)",
       title = "Predicted  RT by Base Frequency, Family Size, and Orthographic Sensitivity")+
  theme( plot.title = element_text(size = 8, hjust = .5),
         legend.title = element_blank(),
         axis.text.x = element_text(size = 8))   
```


